---
title: "Variable Preparations"
description: "Data cleaning and calculation of composite scores" 

format:
  html:
    theme: paper
    shift-heading-level-by: 1
    code-tools: true
    code-fold: true
    toc: true
    toc-fold: false
    toc-location: right
    toc-depth: 3
    toc-title: "Contents"

# Portability settings
embed-resources: true

# Execution options 
execute:
  warning: false
---

```{r}
#| include: false
# set error messages to English
Sys.setenv(LANG = "en")

knitr::opts_chunk$set(
  fig.align = "center", 
  fig.retina = 3,
  fig.width = 6, 
  fig.height = (6 * 0.618),
  out.width = "90%", 
  collapse = FALSE
)

options(
  digits = 4,
  width = 300,
  dplyr.summarise.inform = FALSE)
```

```{r}
#| include: false
#| warning: true
#| message: true
if (!require("groundhog", quietly = TRUE)) {
  install.packages("groundhog")
}
library("groundhog")

# use groundhog to install and load packages
pkgs <- c("here",         # System path management
          "tidyverse",    # ggplot, dplyr, and friends
          "psych",        # Procedures for psychological research, psychometrics
          "tinytable",    # Minimalist tables
          "modelsummary"  # Data and model summaries with tables and plots
          )

groundhog.library(pkgs, "2026-01-01")
```

```{r}
#| include: false
data_dir <- here("01_data")
data_clean_dir <- here("01_data", "clean")
table_dir <- here("02_output", "tables", "descriptives")
figure_dir <- here("02_output", "figures", "descriptives")

dir.create(data_clean_dir, recursive = TRUE, showWarnings = TRUE)
dir.create(table_dir, recursive = TRUE, showWarnings = TRUE)
dir.create(figure_dir, recursive = TRUE, showWarnings = TRUE)
```

```{r}
load(here(data_dir, "raw", "exp_dat_raw.RData"))
```

## Apply Pre-Registered Exclusions

```{r}
initial_sample <- nrow(df_exp)
df_exp <- df_exp |> 
  filter(pre_attention_exclusion == "include")
final_sample <- nrow(df_exp)
```

```{r}
print(paste("N =", initial_sample - final_sample, "participants excluded due to 2 or more failed pre-treatment attention checks. Final analysis n =", final_sample))
```

## Calculate (Composite) Variables

### Factors 

```{r}
df_exp <- df_exp |> 
  mutate(exp_condition = factor(exp_condition, levels = c("control", "hope", "anxiety")),
         age_group = fct_collapse(age_group,
                                  "16-21 years" = c("16 - 17 years", "18 - 21 years"),
                                  "22-26 years" = "22 - 26 years"))
```

### Pre-treatment Scales

#### Political participation 

```{r}
df_exp <- df_exp |>
  mutate(
    polpart_sum = polpart_party + polpart_badge + polpart_petition + 
                  polpart_demonstration + polpart_social_media,
    polpart_pomp = (polpart_sum - 5) / (35 - 5)
  )

df_exp |> 
  select(polpart_pomp, polpart_sum, 
         polpart_party, polpart_badge, polpart_petition, polpart_demonstration, polpart_social_media) |> 
  datasummary_correlation()

df_exp |> 
  select(polpart_pomp, polpart_sum) |> 
  datasummary_skim()
```

McDonald's Omega:
```{r}
polpart_omega <- df_exp |> 
  select(starts_with("polpart_")) |> 
  select(-polpart_sum, -polpart_pomp) |>
  omega(m = _, nfactors = 1)

polpart_omega$omega.tot
```

#### Authoritarian and Democratic Preferences

```{r}
df_exp <- df_exp |>
  mutate(
    aut_sum = aut_strong_leader + aut_strong_government + aut_less_control,
    aut_pomp = (aut_sum - 3) / (21 - 3),
    dem_sum = dem_equal_vote + dem_fundamental_rights + dem_multiple_parties,
    dem_pomp = (dem_sum - 3) / (21 - 3)
  )

df_exp |> 
  select(aut_pomp, aut_sum, 
         aut_strong_leader, aut_strong_government, aut_less_control,
         dem_pomp, dem_sum, 
         dem_equal_vote, dem_fundamental_rights, dem_multiple_parties) |> 
  datasummary_correlation()

df_exp |> 
  select(aut_pomp, aut_sum, dem_pomp, dem_sum) |> 
  datasummary_skim()
```

Mc Donald's Omega
```{r}
aut_omega <- df_exp |> 
  select(starts_with("aut_")) |> 
  select(-aut_sum, -aut_pomp) |>
  omega(nfactors = 1)

aut_omega$omega.tot
```

```{r}
dem_omega <- df_exp |> 
  select(starts_with("dem_")) |> 
  select(-dem_sum, -dem_pomp) |>
  omega(nfactors = 1)

dem_omega$omega.tot
```

#### Emotion Regulation

```{r}
df_exp <- df_exp |>
  mutate(
    cognitive_reappraisal_sum = erq_reappraisal1 + erq_reappraisal2 + erq_reappraisal3 + 
                                erq_reappraisal4 + erq_reappraisal5 + erq_reappraisal6,
    cognitive_reappraisal_pomp = (cognitive_reappraisal_sum - 6) / (42 - 6),
    expressive_suppression_sum = erq_suppression1 + erq_suppression2 + 
                                 erq_suppression3 + erq_suppression4,
    expressive_suppression_pomp = (expressive_suppression_sum - 4) / (28 - 4)
  )

df_exp |> 
  select(cognitive_reappraisal_pomp, cognitive_reappraisal_sum,
         erq_reappraisal1, erq_reappraisal2, erq_reappraisal3,
         erq_reappraisal4, erq_reappraisal5, erq_reappraisal6,
         expressive_suppression_pomp, expressive_suppression_sum,
         erq_suppression1, erq_suppression2, erq_suppression3, erq_suppression4) |> 
  datasummary_correlation()

df_exp |> 
  select(cognitive_reappraisal_pomp, cognitive_reappraisal_sum,
         expressive_suppression_pomp, expressive_suppression_sum) |> 
  datasummary_skim()
```

```{r}
cognitive_reappraisal_omega <- df_exp |> 
  select(starts_with("erq_reappraisal")) |>
  omega(nfactors = 1)

cognitive_reappraisal_omega$omega.tot
```

```{r}
expressive_suppression_omega <- df_exp |> 
  select(starts_with("erq_suppression")) |>
  omega(nfactors = 1)

expressive_suppression_omega$omega.tot
```

#### Ambiguity avoidance

```{r}
df_exp <- df_exp |>
  mutate(
    ambiguity_intolerance_sum = ambiguity1 + ambiguity2 + ambiguity3 + ambiguity4,
    ambiguity_intolerance_pomp = (ambiguity_intolerance_sum - 4) / (28 - 4)
  )

df_exp |> 
  select(ambiguity_intolerance_pomp, ambiguity_intolerance_sum,
         ambiguity1, ambiguity2, ambiguity3, ambiguity4) |> 
  datasummary_correlation()

df_exp |> 
  select(ambiguity_intolerance_pomp, ambiguity_intolerance_sum) |> 
  datasummary_skim()
```

```{r}
ambiguity_intolerance_omega <- df_exp |> 
  select(starts_with("ambiguity")) |>
  select(-ambiguity_intolerance_sum, -ambiguity_intolerance_pomp) |>
  omega(nfactors = 1)

ambiguity_intolerance_omega$omega.tot
```

#### AOT

```{r}
df_exp <- df_exp |>
  mutate(
    across(aot1:aot6, ~ 8 - ., .names = "{.col}_rev"),
    aot_sum = aot1_rev + aot2_rev + aot3_rev + aot4_rev + aot5_rev + aot6_rev,
    aot_pomp = (aot_sum - 6) / (42 - 6)
  )

df_exp |> 
  select(aot_pomp, aot_sum,
         aot1_rev, aot2_rev, aot3_rev, aot4_rev, aot5_rev, aot6_rev) |> 
  datasummary_correlation()

df_exp |> 
  select(aot_pomp, aot_sum) |> 
  datasummary_skim()
```

```{r}
aot_omega <- df_exp |> 
  select(aot1_rev:aot6_rev) |>
  omega(nfactors = 1)

aot_omega$omega.tot
```

## Post-Treatment Scales

#### Experiment Democratic Support

```{r}
df_exp <- df_exp |>
  mutate(
    exp_dem_censor_media_rev = 6 - exp_dem_censor_media,
    exp_dem_one_party_rev = 6 - exp_dem_one_party,
    exp_dem_question_vote_rev = 6 - exp_dem_question_vote,
    exp_dem_ignore_courts_rev = 6 - exp_dem_ignore_courts,
    exp_dem_ignore_parliament_rev = 6 - exp_dem_ignore_parliament,
    exp_dem_bend_law_rev = 6 - exp_dem_bend_law,
    exp_dem_sum = exp_dem_censor_media_rev + exp_dem_one_party_rev + 
                  exp_dem_question_vote_rev + exp_dem_respect_elections +
                  exp_dem_ignore_courts_rev + exp_dem_ignore_parliament_rev + 
                  exp_dem_bend_law_rev,
    exp_dem_pomp = (exp_dem_sum - 7) / (35 - 7)
  )

df_exp |> 
  select(exp_dem_pomp, exp_dem_sum,
         exp_dem_censor_media_rev, exp_dem_one_party_rev, exp_dem_question_vote_rev,
         exp_dem_respect_elections, exp_dem_ignore_courts_rev, 
         exp_dem_ignore_parliament_rev, exp_dem_bend_law_rev) |> 
  datasummary_correlation()

df_exp |> 
  select(exp_dem_pomp, exp_dem_sum) |> 
  datasummary_skim()
```

```{r}
exp_dem_omega <- df_exp |> 
  select(exp_dem_censor_media_rev, exp_dem_one_party_rev, exp_dem_question_vote_rev,
         exp_dem_respect_elections, exp_dem_ignore_courts_rev, 
         exp_dem_ignore_parliament_rev, exp_dem_bend_law_rev) |>
  omega(nfactors = 1)

exp_dem_omega$omega.tot
```

#### Experiment Political Participation 

```{r}
df_exp <- df_exp |>
  mutate(
    exp_polpart_sum = exp_polpart_explain_vote + exp_polpart_share_story +
                            exp_polpart_send_video + exp_polpart_discuss_online +
                            exp_polpart_protest,
    exp_polpart_pomp = (exp_polpart_sum - 5) / (25 - 5)
  )

df_exp |> 
  select(exp_polpart_pomp, exp_polpart_sum,
         exp_polpart_explain_vote, exp_polpart_share_story,
         exp_polpart_send_video, exp_polpart_discuss_online,
         exp_polpart_protest) |> 
  datasummary_correlation()

df_exp |> 
  select(exp_polpart_pomp, exp_polpart_sum) |> 
  datasummary_skim()
```

```{r}
exp_polpart_omega <- df_exp |> 
  select(exp_polpart_explain_vote, exp_polpart_share_story,
         exp_polpart_send_video, exp_polpart_discuss_online,
         exp_polpart_protest) |>
  omega(nfactors = 1)

exp_polpart_omega$omega.tot
```

### Reliability Table 

```{r}
reliability_table <- tibble(
  Scale = c(
    "Political Participation (Pre)",
    "Authoritarianism (Pre)",
    "Democratism (Pre)",
    "Cognitive Reappraisal (Pre)",
    "Expressive Suppression (Pre)",
    "Ambiguity Intolerance (Pre)",
    "Actively Open-Minded Thinking (Pre)",
    "Democratic Support (Post)",
    "Political Participation (Post)"
  ),
  `McDonald's Omega` = c(
    polpart_omega$omega.tot,
    aut_omega$omega.tot,
    dem_omega$omega.tot,
    cognitive_reappraisal_omega$omega.tot,
    expressive_suppression_omega$omega.tot,
    ambiguity_intolerance_omega$omega.tot,
    aot_omega$omega.tot,
    exp_dem_omega$omega.tot,
    exp_polpart_omega$omega.tot
  ),
  `Cronbach's Alpha` = c(
    polpart_omega$alpha,
    aut_omega$alpha,
    dem_omega$alpha,
    cognitive_reappraisal_omega$alpha,
    expressive_suppression_omega$alpha,
    ambiguity_intolerance_omega$alpha,
    aot_omega$alpha,
    exp_dem_omega$alpha,
    exp_polpart_omega$alpha
  )
)

reliability_table |> 
  tt()

reliability_table |> 
  tt() |> 
  save_tt(here(table_dir, "reliability_table.docx"), overwrite = TRUE)
```

## Manipulation Check

```{r}
df_exp <- df_exp |> 
  mutate(anxiety_hope_dim = (exp_check_anxious - exp_check_hopeful + 100) / 200)
```

## Conjoint Experiment

### Code democratic / undemocratic behaviour

```{r}
df_exp <- df_exp |>
  rename_with(
    ~ str_replace(., "^(exp_choice\\d_dem\\d)$", "\\1_raw"),
    matches("^exp_choice\\d_dem\\d$")
  ) |>
  mutate(
    across(
      matches("exp_choice\\d_dem\\d_raw"), 
      ~ case_when(
        str_detect(., "adhered to$") ~ "democratic",
        str_detect(., "preserve existing polling-stations") ~ "democratic",
        str_detect(., "unacceptable to harass journalists") ~ "democratic",
        str_detect(., "unacceptable to fight political opponents") ~ "democratic",
        str_detect(., "should be ignored$") ~ "undemocratic",
        str_detect(., "reduce polling stations") ~ "undemocratic",
        str_detect(., "acceptable to harass journalists") ~ "undemocratic",
        str_detect(., "legitimate to fight political opponents") ~ "undemocratic"
      ),
      .names = "{str_remove(.col, '_raw$')}"
    )
  )
```

```{r}
df_exp |>
  count(exp_choice1_dem1_raw, exp_choice1_dem1) |> 
  tt()
```

## Create final data sets for analysis

### Wide data

```{r}
df_wide <- df_exp |>
  select(
    id, date, duration, sample_type, target_group,
    region, age, age_group, gender, urbanicity, work_situation,
    education, education_level, born_in_country, parents_born_in_country,
    migration_background, living_standard, living_standard_small,
    
    exp_condition, exp_treatment_time, exp_attention,
    
    exp_comment, exp_reaction, exp_share, exp_like,
    
    exp_dem_pomp, 
    exp_dem_censor_media, exp_dem_censor_media_rev, 
    exp_dem_one_party, exp_dem_one_party_rev,
    exp_dem_question_vote, exp_dem_question_vote_rev,
    exp_dem_respect_elections, 
    exp_dem_ignore_courts, exp_dem_ignore_courts_rev,
    exp_dem_ignore_parliament, exp_dem_ignore_parliament_rev,
    exp_dem_bend_law, exp_dem_bend_law_rev,
    
    exp_polpart_pomp,
    exp_polpart_explain_vote, exp_polpart_share_story,
    exp_polpart_send_video, exp_polpart_discuss_online, exp_polpart_protest,
    
    exp_polinfo, exp_polinfo_time,
    
    anxiety_hope_dim, exp_check_anxious, exp_check_angry, 
    exp_check_hopeful, exp_check_happy, exp_check_calm,
    
    starts_with("exp_choice"), starts_with("exp_conjoint"),
    
    exp_design, exp_debriefing,
    
    polpart_pomp, aut_pomp, dem_pomp,
    cognitive_reappraisal_pomp, expressive_suppression_pomp,
    ambiguity_intolerance_pomp, aot_pomp,
    
    left_right, progressive_conservative,
    conservatives_feeling, labour_feeling, libdems_feeling,
    greens_feeling, reform_feeling,
    political_interest, mii, mii_category, mii_category_small,
    
    polpart_sum, polpart_party, polpart_badge, polpart_petition,
    polpart_demonstration, polpart_social_media,
    
    aut_sum, aut_strong_leader, aut_strong_government, aut_less_control,
    
    dem_sum, dem_equal_vote, dem_fundamental_rights, dem_multiple_parties,
    
    cognitive_reappraisal_sum, erq_reappraisal1, erq_reappraisal2,
    erq_reappraisal3, erq_reappraisal4, erq_reappraisal5, erq_reappraisal6,
    
    expressive_suppression_sum, erq_suppression1, erq_suppression2,
    erq_suppression3, erq_suppression4,
    
    ambiguity_intolerance_sum, ambiguity1, ambiguity2, ambiguity3, ambiguity4,
    
    aot_sum, aot1, aot2, aot3, aot4, aot5, aot6,
    aot1_rev, aot2_rev, aot3_rev, aot4_rev, aot5_rev, aot6_rev,
    
    exp_dem_sum, exp_polpart_sum,
    
    pre_attention_exclusion, pre_attention1, pre_attention2, pre_attention3, post_attention1
  )
```

### Long data

```{r}
# Remove uncoded democracy variables
df_long_1 <- df_wide |>
  select(-matches("exp_choice\\d_dem\\d_raw$")) |> 
  mutate(across(matches("exp_choice\\d_age[12]"), as.character)) |> 
  rename(participant_age = age) 

# Create trial-level data
df_long_2 <- df_long_1 |>
  pivot_longer(
    cols = matches("exp_conjoint[1-4]"),
    names_to = "trial",
    values_to = "choice",
    names_pattern = "exp_conjoint(.)"
  ) |>
  mutate(trial = as.integer(trial))

# Stack candidates within trials
df_long_3 <- df_long_2 |>
  pivot_longer(
    cols = matches("exp_choice\\d_(sex|age|party|dem|eco)[12]$"),
    names_to = c("trial_num", "attribute", "candidate"),
    names_pattern = "exp_choice(\\d)_(sex|age|party|dem|eco)([12])$",
    values_to = "level"
  ) |>
  filter(trial == trial_num) |>
  pivot_wider(
    names_from = attribute,
    values_from = level
  ) |>
  select(-trial_num)

# Create candidate labels and preference coding + final renaming
df_long <- df_long_3 |>
  mutate(
    age = as.integer(age),
    candidate_label = paste0("Candidate ", if_else(candidate == "1", "A", "B")),
    conjoint_choice = if_else(candidate_label == choice, 1L, 0L)
  ) |>
  rename(
    conjoint_sex = sex,
    conjoint_age = age,
    conjoint_party = party,
    conjoint_dem = dem,
    conjoint_eco = eco
  ) |>
  select(
    id:exp_dem_bend_law_rev,
    
    trial, candidate, candidate_label, choice, conjoint_choice,
    conjoint_sex, conjoint_age, conjoint_party, conjoint_dem, conjoint_eco,
    
    exp_polpart_pomp:post_attention1
  )
```

## Save analysis data 

```{r}
save(df_wide, file = here(data_clean_dir, "df_wide.RData"))
write_csv(df_wide, file = here(data_clean_dir, "df_wide.csv"))

save(df_long, file = here(data_clean_dir, "df_long.RData"))
write_csv(df_long, file = here(data_clean_dir, "df_long.csv"))
```




