---
title: "Exploratory: Post Engagement"
description: "How did participants react to the posts?" 

format:
  html:
    theme: paper
    shift-heading-level-by: 1
    code-tools: true
    code-fold: true
    toc: true
    toc-fold: false
    toc-location: right
    toc-depth: 4
    toc-title: "Contents"

# Portability settings
embed-resources: true

# Execution options 
execute:
  warning: false
---

```{r}
#| include: false
# set error messages to English
Sys.setenv(LANG = "en")

knitr::opts_chunk$set(
  fig.align = "center", 
  fig.retina = 3,
  fig.width = 6, 
  fig.height = (6 * 0.618),
  out.width = "90%", 
  collapse = FALSE
)

options(
  digits = 4,
  width = 300,
  dplyr.summarise.inform = FALSE)
```

```{r}
#| include: false
#| warning: true
#| message: true
if (!require("groundhog", quietly = TRUE)) {
  install.packages("groundhog")
}
library("groundhog")

# use groundhog to install and load packages
pkgs <- c("here",         # System path management
          "tidyverse",    # ggplot, dplyr, and friends
          "brms",         # Bayesian regression modelling in Stan
          "broom.mixed",  # Tidy model outputs
          "marginaleffects", # Model-based predictions, comparisons, and more marginalia
          "tidybayes",    # Tools to work with Bayesian models 
          "tinytable",    # Minimalist tables
          "rstatix",      # Basic tidy statistical tests 
          "modelsummary", # Data and model summaries with tables and plots
          "marginaleffects", # Model-based predictions, comparisons, and more marginalia
          "ggdist",       # Additional plot elements
          "ggrain",       # For fancy raincloud plots
          "GGally",       # ggpairs and other ggplot2 friends
          "emojifont",    # Emojis in GGPlot2
          "ggsignif",     # Add significance to figures
          "patchwork",    # Combine multiple ggplots
          "showtext"      # Additional fonts for plots etc
          )

groundhog.library(pkgs, "2026-01-01")
```

```{r}
#| include: false
# I use the faster cmdstanr backend for Stan in the place of rstan
# to do so install the cmdstanr package first: https://mc-stan.org/cmdstanr/
# Then run cmdstanr::install_cmdstan() to install cmdstan on your computer.
# RTools must be installed. For more info see 
# https://mc-stan.org/cmdstanr/articles/cmdstanr.html#introduction

# install.packages("cmdstanr", repos = c('https://stan-dev.r-universe.dev', getOption("repos")))
# cmdstanr::install_cmdstan()

options(mc.cores = 4,  
        brms.backend = "cmdstanr")
```

```{r}
#| include: false

showtext_auto()
showtext_opts(dpi = 600)

font_add_google("Public Sans", "Public Sans")
font_add_google("Public Sans", "Public Sans Light", regular.wt = 300)
font_add_google("Public Sans", "Public Sans Semibold", regular.wt = 600)

# Custom ggplot theme
theme_nice <- function(base_size = 14) {
  # General text family and base size
  theme_minimal(base_family = "Public Sans", base_size = base_size) +
    theme(
      # Remove minor grid lines for cleaner look
      panel.grid.minor = element_blank(),
      # Customize major grid lines color
      panel.grid.major = element_blank(),
      # Plot title: bold and custom relative size
      plot.title = element_text(family = "Public Sans", face = "bold", size = rel(1.1), margin = margin(b = 10)),
      # Subtitle and caption: lighter weight 
      plot.subtitle = element_text(family = "Public Sans Light", face = "plain"),
      plot.caption = element_text(family = "Public Sans Light", face = "plain"),
      # Axis text: Relative size
      axis.text = element_text(size = rel(0.9)),
      # Axis titles: Semibold and custom relative size
      axis.title = element_text(family = "Public Sans Semibold", size = rel(0.9)),
      axis.title.x = element_text(hjust = 0.5),
      axis.title.y = element_text(hjust = 0.5),
      # Axis lines
      axis.line = element_line(color = "grey25", linewidth = 0.8),
      # Facet labels: bold text on grey background
      strip.text = element_text(
        family = "Public Sans Semibold", face = "plain",
        size = rel(1),
        hjust = 0.5
      ),
      strip.background = element_rect(fill = "grey95", color = "grey25", linewidth = 0.8), 
      # Legend styling: compact and top-positioned
      legend.title = element_text(family = "Public Sans Semibold", size = rel(0.8)),
      legend.text = element_text(size = rel(0.8)),
      legend.position = "top",
      legend.justification = "center",
      legend.title.position = "left",
      legend.margin = margin(l = 0, t = 0)
    )
}


theme_set(theme_nice())
update_geom_defaults("text", list(family = "Public Sans"))
update_geom_defaults("label", list(family = "Public Sans"))
```

```{r}
#| include: false
data_dir <- here("01_data")
table_dir <- here("02_output", "tables", "exploratory")
figure_dir <- here("02_output", "figures", "exploratory")

dir.create(table_dir, recursive = TRUE, showWarnings = TRUE)
dir.create(figure_dir, recursive = TRUE, showWarnings = TRUE)
```

```{r}
load(here(data_dir, "analysis", "df_wide.RData"))
df <- df_wide 
rm(df_wide)
```

## Manipulation Checks

```{r}
manip_balance_table <- df |> 
  select(Treatment = exp_condition,
         "Anxiety-Hope" = anxiety_hope_dim,
         "Anxiety Rating" = exp_check_anxious,
         "Angry Rating" = exp_check_angry,
         "Hopeful Rating" = exp_check_hopeful,
         "Happy Rating" = exp_check_happy,
         "Calm Rating" = exp_check_calm,
         "Comment Sentiment" = exp_comment_sentiment) |> 
  mutate(Treatment = factor(Treatment, levels = c("anxiety", "hope", "control"), 
                            labels = c("Anxiety", "Hope", "Control"))) |> 
  datasummary_balance(~Treatment, 
                      data = _,
                      fmt = 2)

manip_balance_table |> 
  save_tt(here(table_dir, "manipulation_balance.docx"), overwrite = TRUE)

manip_balance_table
```

```{r}
#| fig-height: 5
#| fig-width: 8
#| fig-showtext: TRUE
manip_check_data <- df |>
  select(id, exp_condition, starts_with("exp_check")) |>
  pivot_longer(
    cols = starts_with("exp_check"),
    names_to = "emotion",
    values_to = "rating",
    names_prefix = "exp_check_"
  ) |>
  mutate(
    emotion = factor(emotion, 
                     levels = c("angry", "anxious", "hopeful", "happy", "calm"), 
                     labels = c("Angry", "Anxious", "Hopeful", "Happy", "Calm"))
  )

# Define emotion colors
emotion_colors <- c(
  "Angry" = "#e07a7a",
  "Anxious" = "#f4a582",
  "Hopeful" = "#a8ddb5",
  "Happy" = "#ffd97d",
  "Calm" = "#7eb3d4"
)

manip_check_data |> 
  ggplot(aes(x = exp_condition, y = rating, fill = emotion)) +
  geom_boxplot(
    position = position_dodge(width = 0.9),
    width = 0.6,
    outlier.size = 0.8,
    outlier.alpha = 0.3
  ) +
  scale_fill_manual(
    values = emotion_colors,
    name = "Emotion"
  ) +
  scale_x_discrete(
    labels = c("anxiety" = "Anxiety", "hope" = "Hope", "control" = "Control")
  ) +
  scale_y_continuous(
    limits = c(-10, 110),
    breaks = seq(0, 100, 20),
    expand = c(0.05, 0.05)
  ) +
  labs(
    x = "Experimental Condition",
    y = "Emotion Rating (0-100)",
    subtitle = "Thinking back to the Instagram post that you saw earlier, 
to what extent did the post make you feel …"
  ) +
  theme_nice() +
  guides(fill = guide_legend(override.aes = list(shape = NA)))

ggsave(here(figure_dir, "manipulation_check.svg"),
       height = 5,
       width = 8,
       dpi = 600)
```

```{r}
manip_pairwise <- manip_check_data |>
  group_by(emotion) |>
  pairwise_t_test(
    rating ~ exp_condition,
    detailed = TRUE,
    pool.sd = FALSE,
    p.adjust.method = "holm",
    ref.group = "control"
  ) |>
  ungroup()

manip_pairwise_table <- manip_pairwise |>
  select(Emotion = emotion, 
         `Group 1` = group1, 
         `Group 2` = group2, 
         `Mean 1` = estimate1,
         `Mean 2` = estimate2, 
         `Estimate` = estimate,
         # "95% CI Low" = conf.low,
         # "95% CI High" = conf.high, 
         p, p.adj,
         # p.adj.signif,
         df) |>
  mutate(across(where(is.numeric), \(x) round(x, 3))) |> 
  tt()

manip_pairwise_table

manip_pairwise_table |> 
  save_tt(here(table_dir, "manipulation_pairwise.docx"), overwrite = TRUE)
```

```{r}
# Helper function to create correlogram
scatter_function_grouped <- function(data, mapping, ...) {
  ggplot(data = data, mapping = mapping) +
    geom_point(alpha = 0.2, size = 1) +
    geom_smooth(method = "lm", 
                se = TRUE, 
                linewidth = 1.2, 
                alpha = 0.5, 
                na.rm = TRUE)
}
```

```{r}
#| warning: false
#| message: false
#| fig-height: 12
#| fig-width: 16
#| fig-showtext: TRUE
df |> 
  mutate(age_group = as.character(age_group)) |> 
  mutate(age_group = case_match(age_group,
    "16-21 years" ~ "16-21",
    "22-26 years" ~ "22-26"
  )) |> 
  select(
    age_group,
    age,
    "a-h" = anxiety_hope_dim,
    agr = exp_check_angry,
    axy = exp_check_anxious,
    hop = exp_check_hopeful,
    hap = exp_check_happy,
    cal = exp_check_calm,
    sent = exp_comment_sentiment,
    exp_dem = exp_dem_pomp,
    exp_polpart = exp_polpart_pomp
  ) |> 
  ggpairs(
    data = _,
    columns = 2:11,  
    mapping = aes(color = age_group),
    lower = list(continuous = scatter_function_grouped),
    upper = list(continuous = wrap("cor", stars = TRUE, size = 4)),  
    diag = list(continuous = wrap("densityDiag", alpha = 0.5)),
    legend = 1,
    progress = FALSE
  ) +
  scale_color_manual(values = c("16-21" = "#1b9e77",
                                "22-26" = "#d95f02")) +
  scale_fill_manual(values = c("16-21" = "#1b9e77",
                                "22-26" = "#d95f02")) +
  theme_nice() +
  theme(legend.text = element_text(size = 16),
        legend.title = element_text(size = 16)) + 
  labs(color = "age_group", fill = "age_group")

ggsave(here(figure_dir, "manip_correlogram.svg"),
       height = 12,
       width = 16,
       dpi = 600)
```

## Time Spent Viewing the Post


## Comments, Liking, Sharing

```{r}
df |> 
  select(Treatment = exp_condition,
         exp_comment_emotion,
         exp_reaction, 
         exp_like, 
         exp_share) |> 
  mutate(Treatment = factor(Treatment, levels = c("anxiety", "hope", "control"), 
                            labels = c("Anxiety", "Hope", "Control"))) |> 
  datasummary_balance(~Treatment, 
                      data = _)
```


### Sharing of Post

```{r}
#| fig-height: 4
#| fig-width: 6
#| fig-showtext: TRUE
df |> 
  mutate(exp_share = as.numeric(exp_share)) |> 
  ggplot(aes(x = exp_condition, y = exp_share, fill = exp_condition, color = exp_condition)) +
  geom_rain(
    rain.side = "r",  
    seed = 42,
    point.args = list(alpha = 0.2, size = 0.8),  
    boxplot.args = list(
      outlier.shape = NA,
      alpha = 0.7,
      color = "black"  
    ),
    violin.args = list(alpha = 0.7)
  ) +
  geom_signif(
    aes(x = exp_condition, y = exp_share),  
    comparisons = list(
      c("anxiety", "hope"), 
      c("anxiety", "control"), 
      c("hope", "control")
    ),
    map_signif_level = TRUE,
    size = 0.8,
    textsize = 4,
    family = "Public Sans",
    color = "black",
    tip_length = 0,
    step_increase = 0.12,
    inherit.aes = FALSE
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))) +
  labs(
    x = NULL,
    y = "1-5 Likert Scale",
    title = "Likelihood to Share Post by Experimental Condition"
  ) +
  theme_nice() +
  theme(legend.position = "none") 

ggsave(here(figure_dir, "share_raincloud.svg"),
       height = 4,
       width = 6,
       dpi = 600)
```

```{r}
share_pairwise <- df |>
  mutate(exp_share = as.numeric(exp_share)) |>
  pairwise_t_test(
    exp_share ~ exp_condition,
    detailed = TRUE,
    pool.sd = FALSE,
    p.adjust.method = "holm",
    # ref.group = "control"
  ) 

share_pairwise_table <- share_pairwise |>
  select(`Group 1` = group1,
         `Group 2` = group2,
         `Mean 1` = estimate1,
         `Mean 2` = estimate2,
         `Estimate` = estimate,
         # "95% CI Low" = conf.low,
         # "95% CI High" = conf.high,
         p, p.adj,
         # p.adj.signif,
         df) |>
  mutate(across(where(is.numeric), \(x) round(x, 3))) |>
  tt()

share_pairwise_table

share_pairwise_table |>
  save_tt(here(table_dir, "share_pairwise.docx"), overwrite = TRUE)
```

### Liking of Post

```{r}
#| fig-height: 4
#| fig-width: 6
#| fig-showtext: TRUE
df |> 
  mutate(exp_like = as.numeric(exp_like)) |> 
  ggplot(aes(x = exp_condition, y = exp_like, fill = exp_condition, color = exp_condition)) +
  geom_rain(
    rain.side = "r",  
    seed = 42,
    point.args = list(alpha = 0.2, size = 0.8),  
    boxplot.args = list(
      outlier.shape = NA,
      alpha = 0.7,
      color = "black"  
    ),
    violin.args = list(alpha = 0.7)
  ) +
  geom_signif(
    aes(x = exp_condition, y = exp_like),  
    comparisons = list(
      c("anxiety", "hope"), 
      c("anxiety", "control"), 
      c("hope", "control")
    ),
    map_signif_level = TRUE,
    size = 0.8,
    textsize = 4,
    family = "Public Sans",
    color = "black",
    tip_length = 0,
    step_increase = 0.12,
    inherit.aes = FALSE
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))) +
  labs(
    x = NULL,
    y = "1-5 Likert Scale",
    title = "Likelihood to Like Post by Experimental Condition"
  ) +
  theme_nice() +
  theme(legend.position = "none") 

ggsave(here(figure_dir, "like_raincloud.svg"),
       height = 4,
       width = 6,
       dpi = 600)
```

```{r}
like_pairwise <- df |>
  mutate(exp_like = as.numeric(exp_like)) |>
  pairwise_t_test(
    exp_like ~ exp_condition,
    detailed = TRUE,
    pool.sd = FALSE,
    p.adjust.method = "holm",
    # ref.group = "control"
  ) 

like_pairwise_table <- like_pairwise |>
  select(`Group 1` = group1,
         `Group 2` = group2,
         `Mean 1` = estimate1,
         `Mean 2` = estimate2,
         `Estimate` = estimate,
         # "95% CI Low" = conf.low,
         # "95% CI High" = conf.high,
         p, p.adj,
         # p.adj.signif,
         df) |>
  mutate(across(where(is.numeric), \(x) round(x, 3))) |>
  tt()

like_pairwise_table

like_pairwise_table |>
  save_tt(here(table_dir, "like_pairwise.docx"), overwrite = TRUE)
```

## Exploratory Manipulation Check Models

```{r}
# brms settings
bayes_seed <- 42
chains <- 4
iter <- 4000
warmup <- floor(iter/2)
adapt_delta <- 0.90
max_treedepth <- 10
```

```{r}
# marginaleffects settings
options(marginaleffects_posterior_interval = "hdi")
options(marginaleffects_posterior_center = stats::median)
```

```{r}
df_mod <- df |> 
  mutate(across(c(exp_share, exp_like), as.numeric)) |> 
  mutate(exp_share_pomp = (exp_share - 1) / 4,
         exp_like_pomp = (exp_like - 1) / 4,
         comment_sentiment_pomp = (exp_comment_sentiment - 1) / 6,
         Anxious = exp_check_anxious / 100,
         Angry = exp_check_angry / 100,
         Hopeful = exp_check_hopeful / 100,
         Happy = exp_check_happy / 100,
         Calm = exp_check_calm / 100)
```


```{r}
priors <- c(
  prior(normal(0.5, 0.5), class = "Intercept"),
  prior(normal(0, 0.5), class = "b"),
  prior(exponential(4), class = "sigma"))
```

### Anxiety-Hope Dimension

```{r}
#| output: false
ah1 <- brm(
  data = df_mod,
  family = gaussian(),
  formula = anxiety_hope_dim ~ exp_condition,
  prior = priors,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth)
  )
```

```{r}
print(ah1)
```
### Sentiment

```{r}
#| output: false
sent1 <- brm(
  data = df_mod,
  family = gaussian(),
  formula = comment_sentiment_pomp ~ exp_condition,
  prior = priors,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth)
  )
```

```{r}
print(sent1)
```
### Sharing of Post

```{r}
#| output: false
share1 <- brm(
  data = df_mod,
  family = gaussian(),
  formula = exp_share_pomp ~ exp_condition,
  prior = priors,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth)
  )
```

```{r}
print(share1)
```

### Liking of Post

```{r}
#| output: false
like1 <- brm(
  data = df_mod,
  family = gaussian(),
  formula = exp_like_pomp ~ exp_condition,
  prior = priors,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth)
  )
```

```{r}
print(like1)
```

### Emotion Ratings

```{r}
# Create formula with set_rescor
f_er1 <- bf(mvbind(Anxious, Angry, Hopeful, Happy, Calm) ~ exp_condition) + 
  set_rescor(FALSE)

# Specify priors for each response variable
priors_er1 <- c(
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Anxious"),
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Angry"),
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Hopeful"),
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Happy"),
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Calm"),
  prior(normal(0, 0.5), class = "b", resp = "Anxious"),
  prior(normal(0, 0.5), class = "b", resp = "Angry"),
  prior(normal(0, 0.5), class = "b", resp = "Hopeful"),
  prior(normal(0, 0.5), class = "b", resp = "Happy"),
  prior(normal(0, 0.5), class = "b", resp = "Calm"),
  prior(exponential(4), class = "sigma", resp = "Anxious"),
  prior(exponential(4), class = "sigma", resp = "Angry"),
  prior(exponential(4), class = "sigma", resp = "Hopeful"),
  prior(exponential(4), class = "sigma", resp = "Happy"),
  prior(exponential(4), class = "sigma", resp = "Calm")
)
```


```{r}
#|output: false
er1 <- brm(
  data = df_mod,
  family = gaussian(),
  formula = f_er1,
  prior = priors_er1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth
  )
)
```

```{r}
print(er1)
```

## Visualise

### Part 1

```{r}
# Prepare predictions for all models
models_list <- list(
  ah1 = ah1,
  sent1 = sent1,
  share1 = share1,
  like1 = like1
)

outcome_labels <- c(
  ah1 = "Anxiety-Hope Dimension",
  sent1 = "Comment Sentiment",
  share1 = "Likelihood to Share",
  like1 = "Likelihood to Like"
)

predictions <- map_dfr(names(models_list), function(model_name) {
  expand_grid(
    exp_condition = c("control", "anxiety", "hope")
  ) |>
    add_epred_draws(models_list[[model_name]], re_formula = NA, ndraws = 4000) |>
    ungroup() |>
    mutate(
      outcome = model_name,
      outcome_label = outcome_labels[model_name],
      .epred = .epred * 100  # Convert to percentage points
    )
})

# Calculate pairwise contrasts and check if they exclude zero
contrasts <- predictions |>
  select(outcome, outcome_label, exp_condition, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    anxiety_vs_control = anxiety - control,
    hope_vs_control = hope - control,
    anxiety_vs_hope = anxiety - hope
  )

contrast_summary <- contrasts |>
  group_by(outcome, outcome_label) |>
  summarise(
    across(
      c(anxiety_vs_control, hope_vs_control, anxiety_vs_hope),
      list(
        lower = ~hdi(.x, .width = 0.95)[[1]],
        upper = ~hdi(.x, .width = 0.95)[[2]]
      ),
      .names = "{.col}_{.fn}"
    ),
    .groups = "drop"
  ) |>
  mutate(
    anxiety_diff_control = sign(anxiety_vs_control_lower) == sign(anxiety_vs_control_upper),
    hope_diff_control = sign(hope_vs_control_lower) == sign(hope_vs_control_upper),
    anxiety_diff_hope = sign(anxiety_vs_hope_lower) == sign(anxiety_vs_hope_upper)
  )

# Generate compact letter display
cld_labels <- contrast_summary |>
  mutate(
    control_label = case_when(
      # Intransitivity: control bridges anxiety and hope
      !anxiety_diff_control & !hope_diff_control & anxiety_diff_hope ~ "ab",
      TRUE ~ "a"
    ),
    anxiety_label = case_when(
      # Anxiety bridges control and hope
      !anxiety_diff_control & hope_diff_control & !anxiety_diff_hope ~ "ab",
      # Anxiety same as control
      !anxiety_diff_control & !anxiety_diff_hope              ~ "a",
      !anxiety_diff_control & anxiety_diff_hope               ~ "a",
      # Anxiety differs from control
      anxiety_diff_control  & !anxiety_diff_hope              ~ "b",
      anxiety_diff_control  & anxiety_diff_hope               ~ "b"
    ),
    hope_label = case_when(
      # Hope bridges control and anxiety
      !hope_diff_control & !anxiety_diff_hope & anxiety_diff_control  ~ "ab",
      # Intransitivity: hope=b (control bridges)
      !hope_diff_control & anxiety_diff_hope  & !anxiety_diff_control ~ "b",
      # All same
      !hope_diff_control & !anxiety_diff_hope & !anxiety_diff_control ~ "a",
      # Hope~control, anxiety differs from both
      !hope_diff_control & anxiety_diff_hope  & anxiety_diff_control  ~ "a",
      # Hope differs from control
      hope_diff_control  & !anxiety_diff_hope                         ~ "b",
      hope_diff_control  & anxiety_diff_hope  ~ if_else(anxiety_diff_control, "c", "b")
    )
  ) |>
  select(outcome, outcome_label, control_label, anxiety_label, hope_label) |>
  pivot_longer(
    cols = c(control_label, anxiety_label, hope_label),
    names_to = "condition",
    values_to = "cld"
  ) |>
  mutate(exp_condition = str_remove(condition, "_label")) |>
  select(outcome, outcome_label, exp_condition, cld)

# Combine plotting data with CLD labels
plot_data <- predictions |>
  left_join(cld_labels, by = c("outcome", "outcome_label", "exp_condition"))

# Check the CLD labels
cld_labels |> 
  pivot_wider(names_from = exp_condition, values_from = cld) |>
  arrange(outcome)
```

```{r}
part1 <- plot_data |>
  mutate(
    outcome_label = factor(
      outcome_label,
      levels = c("Anxiety-Hope Dimension", "Comment Sentiment", 
                 "Likelihood to Share", "Likelihood to Like")
    ),
    exp_condition = factor(
      exp_condition,
      levels = c("hope", "anxiety", "control"),
      labels = c("Hope", "Anxiety", "Control")
    )
  ) |>
  ggplot(aes(x = .epred, y = exp_condition, fill = exp_condition)) +
  stat_halfeye(
    .width = c(0.95, 0.66),
    point_interval = "median_qi",
    alpha = 0.8,
    height = 0.8
  ) +
  geom_text(
    data = plot_data |>
      mutate(
        outcome_label = factor(
          outcome_label,
          levels = c("Anxiety-Hope Dimension", "Comment Sentiment",
                     "Likelihood to Share", "Likelihood to Like")
        ),
        exp_condition = factor(
          exp_condition,
          levels = c("hope", "anxiety", "control"),
          labels = c("Hope", "Anxiety", "Control")
        )
      ) |>
      group_by(outcome_label, exp_condition, cld) |>
      summarise(x_pos = max(.epred) + 2, .groups = "drop"),
    aes(x = x_pos, y = exp_condition, label = cld),
    size = 4,
    fontface = "bold",
    inherit.aes = FALSE
  ) +
  geom_vline(xintercept = 50, linetype = "dashed", color = "gray40", linewidth = 0.4) +
  facet_wrap(~outcome_label, scales = "free_x", ncol = 2, labeller = labeller(label_both)) +
  scale_fill_manual(
    values = c("Anxiety" = "#AA3377", "Hope" = "#66CCEE", "Control" = "#BBBBBB")
  ) +
  scale_x_continuous(limits = c(25, 75), breaks = seq(20, 80, by = 10)) +
  labs(
    x = "Percentage Points",
    y = NULL,
    title = "Manipulation Check & Post Engagement",
    tag = "I."
  ) +
  theme_nice() +
  theme(
    legend.position = "none",
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2),
    strip.text = element_text(hjust = 0.5, size = rel(0.95)),
    plot.title = element_text(family = "Public Sans", face = "bold", size = rel(1), margin = margin(b = 5))
  )

part1

ggsave(here(figure_dir, "manip_engagement_fig.svg"),
       height = 5,
       width = 6,
       dpi = 600)
```

### Part 2

```{r}
# Extract predictions for all emotions
emotion_predictions <- expand_grid(
  exp_condition = c("control", "anxiety", "hope")
) |>
  add_epred_draws(er1, re_formula = NA, ndraws = 4000) |>
  ungroup() |>
  mutate(.epred = .epred * 100)

# Calculate pairwise contrasts
emotion_contrasts <- emotion_predictions |>
  select(.category, exp_condition, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    anxiety_vs_control = anxiety - control,
    hope_vs_control = hope - control,
    anxiety_vs_hope = anxiety - hope
  )

emotion_contrast_summary <- emotion_contrasts |>
  group_by(.category) |>
  summarise(
    across(
      c(anxiety_vs_control, hope_vs_control, anxiety_vs_hope),
      list(
        lower = ~hdi(.x, .width = 0.95)[[1]],
        upper = ~hdi(.x, .width = 0.95)[[2]]
      ),
      .names = "{.col}_{.fn}"
    ),
    .groups = "drop"
  ) |>
  mutate(
    anxiety_diff_control = sign(anxiety_vs_control_lower) == sign(anxiety_vs_control_upper),
    hope_diff_control = sign(hope_vs_control_lower) == sign(hope_vs_control_upper),
    anxiety_diff_hope = sign(anxiety_vs_hope_lower) == sign(anxiety_vs_hope_upper)
  )

# Generate compact letter display
emotion_cld <- emotion_contrast_summary |>
  mutate(
    control_label = case_when(
      !anxiety_diff_control & !hope_diff_control & anxiety_diff_hope ~ "ab",
      TRUE ~ "a"
    ),
    anxiety_label = case_when(
      !anxiety_diff_control & hope_diff_control & !anxiety_diff_hope ~ "ab",
      !anxiety_diff_control & !anxiety_diff_hope                     ~ "a",
      !anxiety_diff_control & anxiety_diff_hope                      ~ "a",
      anxiety_diff_control  & !anxiety_diff_hope                     ~ "b",
      anxiety_diff_control  & anxiety_diff_hope                      ~ "b"
    ),
    hope_label = case_when(
      !hope_diff_control & !anxiety_diff_hope & anxiety_diff_control  ~ "ab",
      !hope_diff_control & anxiety_diff_hope  & !anxiety_diff_control ~ "b",
      !hope_diff_control & !anxiety_diff_hope & !anxiety_diff_control ~ "a",
      !hope_diff_control & anxiety_diff_hope  & anxiety_diff_control  ~ "a",
      hope_diff_control  & !anxiety_diff_hope                         ~ "b",
      hope_diff_control  & anxiety_diff_hope  ~ if_else(anxiety_diff_control, "c", "b")
    )
  ) |>
  select(.category, control_label, anxiety_label, hope_label) |>
  pivot_longer(
    cols = c(control_label, anxiety_label, hope_label),
    names_to = "condition",
    values_to = "cld"
  ) |>
  mutate(exp_condition = str_remove(condition, "_label")) |>
  select(.category, exp_condition, cld)

# Combine plotting data
emotion_plot_data <- emotion_predictions |>
  left_join(emotion_cld, by = c(".category", "exp_condition"))

# Set colors
# emotion_colors <- c(
#   "Anxious" = "#CC3311",
#   "Angry" = "#EE7733",
#   "Calm" = "#009988",
#   "Hopeful" = "#33BBEE",
#   "Happy" = "#0077BB"
# )

emotion_colors <- c(
  "Anxious" = "#AA3377",
  "Angry" = "#EE6677",
  "Calm" = "#CCBB44",
  "Hopeful" = "#66CCEE",
  "Happy" = "#4477AA"
)

```

```{r}
part2 <- emotion_plot_data |>
  mutate(
    emotion = factor(
      .category,
      levels = c("Anxious", "Angry", "Calm", "Hopeful", "Happy"),
      labels = c("Anxious", "Angry", "Calm", "Hopeful", "Happy")
    ),
    exp_condition = factor(
      exp_condition,
      levels = c("control", "anxiety", "hope"),
      labels = c("Control", "Anxiety", "Hope")
    )
  ) |>
  ggplot(aes(x = exp_condition, y = .epred, color = emotion, group = emotion)) +
  stat_pointinterval(
    .width = 0.95,
    point_interval = "median_hdi",
    position = position_dodge(width = 0.4),
    point_size = 3,
    linewidth = 2
  ) +
  geom_text(
    data = emotion_plot_data |>
      mutate(
        emotion = factor(
          .category,
          levels = c("Anxious", "Angry", "Calm", "Hopeful", "Happy"),
          labels = c("Anxious", "Angry", "Calm", "Hopeful", "Happy")
        ),
        exp_condition = factor(
          exp_condition,
          levels = c("control", "anxiety", "hope"),
          labels = c("Control", "Anxiety", "Hope")
        )
      ) |>
      group_by(emotion, exp_condition, cld) |>
      summarise(y_pos = max(.epred) + 0.5, .groups = "drop"),
    aes(x = exp_condition, y = y_pos, label = cld, color = emotion),
    position = position_dodge(width = 0.4),
    size = 3.5,
    fontface = "bold",
    show.legend = FALSE
  ) +
  scale_y_continuous(limits = c(30, 70), breaks = seq(20, 80, by = 10)) +
  scale_color_manual(
    values = emotion_colors,
    name = NULL
  ) +
  labs(
    x = NULL,
    y = NULL,
    title = "Emotion Ratings in Different Conditions",
    tag = "II."
  ) +
  theme_nice() +
  theme(
    # legend.position = "bottom",
    plot.title = element_text(size = rel(1)),
    panel.grid.major.y = element_line(color = "grey90", linewidth = 0.2),
    legend.text = element_text(size = rel(0.9))
  )

part2

ggsave(here(figure_dir, "manip_emotions_fig.svg"),
       height = 3.5,
       width = 6,
       dpi = 600)
```

### Part 3

```{r}
load.emojifont('OpenSansEmoji.ttf')

reaction_plot_data <- df_mod |>
  filter(!is.na(exp_reaction)) |>
  mutate(
    exp_condition = factor(
      exp_condition,
      levels = c("control", "anxiety", "hope"),
      labels = c("Control", "Anxiety", "Hope")
    ),
    exp_reaction = factor(
      exp_reaction,
      levels = c("Happy", "Hopeful", "Calm", "Angry", "Anxious")
    )
  ) |>
  count(exp_condition, exp_reaction) |>
  group_by(exp_condition) |>
  mutate(
    total = sum(n),
    pct = n / total * 100,
    emoji_icon = case_when(
      exp_reaction == "Angry" ~ emoji("rage"),
      exp_reaction == "Anxious" ~ emoji("fearful"),
      exp_reaction == "Calm" ~ emoji("relieved"),
      exp_reaction == "Hopeful" ~ emoji("blush"),
      exp_reaction == "Happy" ~ emoji("grin")
    ),
    label = if_else(pct >= 1, paste0(emoji_icon, "\n", sprintf("%.0f%%", pct)), "")
  ) |>
  ungroup()
```


```{r}
part3 <- reaction_plot_data |>
  ggplot(aes(x = pct, y = exp_condition, fill = exp_reaction)) +
  geom_col(position = "stack", width = 0.7, color = "grey20") +
  geom_text(
    aes(label = label),
    position = position_stack(vjust = 0.5),
    size = 4,
    family = "OpenSansEmoji",
    color = "black"
  ) +
  scale_fill_manual(
    values = emotion_colors,
    labels = c(
      "Anxious" = emoji("fearful"),
      "Angry" = emoji("rage"),
      "Calm" = emoji("relieved"),
      "Hopeful" = emoji("blush"),
      "Happy" = emoji("grin")
    ),
    name = NULL
  ) +
  scale_x_continuous(
    labels = scales::percent_format(scale = 1),
    expand = c(0, 0)
  ) +
  labs(
    x = NULL,
    y = NULL,
    title = "Emoji Reactions to Post",
    tag = "III."
  ) +
  theme_nice() +
  theme(
    axis.line.x = element_blank(),
    axis.line.y = element_blank(),
    axis.text.x = element_blank(),
    legend.text = element_text(family = "OpenSansEmoji", size = 20)
  ) +
  guides(fill = guide_legend(reverse = TRUE))

part3

ggsave(here(figure_dir, "reaction_emotions_fig.svg"),
       height = 4,
       width = 6.5,
       dpi = 600)
```

### Grid

```{r}
#| fig-height: 8
#| fig-width: 12
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)
(part1 | (part2 / part3)) 

ggsave(here(figure_dir, "manip_grid.png"),
       height = 8,
       width = 12,
       dpi = 600)
```

## Heterogeneity in Emotional Effects 

### Anxiety-Hope x Age Group

```{r}
#| output: false
ah2 <- brm(
  data = df_mod,
  family = gaussian(),
  formula = anxiety_hope_dim ~ exp_condition * age_group,
  prior = priors,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth)
  )
```

```{r}
ah2_brms <- tidy(ah2, robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE) |>
  filter(effect == "fixed") |>
  mutate(term = case_when(
    term == "(Intercept)"                                ~ "Intercept",
    term == "exp_conditionhope"                         ~ "Hope (vs. Control)",
    term == "exp_conditionanxiety"                      ~ "Anxiety (vs. Control)",
    term == "age_group22M26years"                       ~ "Age Group 22-26 (vs. 16-21)",
    term == "exp_conditionhope:age_group22M26years"     ~ "Age Group x Hope",
    term == "exp_conditionanxiety:age_group22M26years"  ~ "Age Group x Anxiety",
    TRUE ~ term
  )) |>
  select(Term = term,
         Median = estimate,
         MAD = std.error,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         "R-hat" = rhat,
         ESS = ess)
```
```{r}
ah2_brms_table <- ah2_brms |>
  mutate(across(where(is.numeric), \(x) round(x, 3))) |>
  tt()

ah2_brms_table
ah2_brms_table |>
  save_tt(here(table_dir, "ah2_brms_table.docx"), overwrite = TRUE)
```

### Anxiety-Hope x Gender

```{r}
#| output: false
ah3 <- brm(
  data = df_mod,
  family = gaussian(),
  formula = anxiety_hope_dim ~ exp_condition * gender,
  prior = priors,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth)
  )
```

```{r}
ah3_brms <- tidy(ah3, robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE) |>
  filter(effect == "fixed") |>
  mutate(term = case_when(
    term == "(Intercept)"                          ~ "Intercept",
    term == "exp_conditionhope"                    ~ "Hope (vs. Control)",
    term == "exp_conditionanxiety"                 ~ "Anxiety (vs. Control)",
    term == "genderfemale"                         ~ "Women (vs. Men)",
    term == "genderother"                          ~ "Other (vs. Men)",
    term == "exp_conditionhope:genderfemale"       ~ "Women x Hope",
    term == "exp_conditionanxiety:genderfemale"    ~ "Women x Anxiety",
    term == "exp_conditionhope:genderother"        ~ "Other x Hope",
    term == "exp_conditionanxiety:genderother"     ~ "Other x Anxiety",
    TRUE ~ term
  )) |>
  select(Term = term,
         Median = estimate,
         MAD = std.error,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         "R-hat" = rhat,
         ESS = ess)
```

```{r}
ah3_brms_table <- ah3_brms |>
  mutate(across(where(is.numeric), \(x) round(x, 3))) |>
  tt()

ah3_brms_table
ah3_brms_table |>
  save_tt(here(table_dir, "ah3_brms_table.docx"), overwrite = TRUE)
```

### All Emotions x Age Group 

```{r}
f_er2 <- bf(mvbind(Anxious, Angry, Hopeful, Happy, Calm) ~ exp_condition * age_group) + 
  set_rescor(FALSE)

priors_er2 <- c(
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Anxious"),
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Angry"),
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Hopeful"),
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Happy"),
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Calm"),
  prior(normal(0, 0.5), class = "b", resp = "Anxious"),
  prior(normal(0, 0.5), class = "b", resp = "Angry"),
  prior(normal(0, 0.5), class = "b", resp = "Hopeful"),
  prior(normal(0, 0.5), class = "b", resp = "Happy"),
  prior(normal(0, 0.5), class = "b", resp = "Calm"),
  prior(exponential(4), class = "sigma", resp = "Anxious"),
  prior(exponential(4), class = "sigma", resp = "Angry"),
  prior(exponential(4), class = "sigma", resp = "Hopeful"),
  prior(exponential(4), class = "sigma", resp = "Happy"),
  prior(exponential(4), class = "sigma", resp = "Calm")
)
```

```{r}
#|output: false
er2 <- brm(
  data = df_mod,
  family = gaussian(),
  formula = f_er2,
  prior = priors_er2,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth
  )
)
```

#### Create Table

```{r}
emotions <- c("Anxious", "Angry", "Hopeful", "Happy", "Calm")

er2_brms_raw <- map(emotions, \(em) {
  tidy(er2, parameters = paste0("^b_", em), robust = TRUE, 
       conf.method = "HPDinterval", rhat = TRUE, ess = TRUE) |>
    mutate(Outcome = em,
           term = str_remove(term, paste0("b_", em, "_")))
}) |>
  list_rbind()

er2_brms <- er2_brms_raw |>
  mutate(term = case_when(
    term == "(Intercept)"                                ~ "Intercept",
    term == "exp_conditionhope"                         ~ "Hope (vs. Control)",
    term == "exp_conditionanxiety"                      ~ "Anxiety (vs. Control)",
    term == "age_group22M26years"                       ~ "Age Group 22-26 (vs. 16-21)",
    term == "exp_conditionhope:age_group22M26years"     ~ "Age Group x Hope",
    term == "exp_conditionanxiety:age_group22M26years"  ~ "Age Group x Anxiety",
    TRUE ~ term
  )) |>
  select(Outcome, Term = term,
         Median = estimate,
         MAD = std.error,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         "R-hat" = rhat,
         ESS = ess)
```

```{r}
er2_brms_table <- er2_brms |>
  mutate(across(where(is.numeric), \(x) round(x, 3))) |>
  select(-Outcome) |>
  tt() |>
  group_tt(i = list(
    "Anxious" = 1,
    "Angry"   = 7,
    "Hopeful" = 13,
    "Happy"   = 19,
    "Calm"    = 25
  ))

er2_brms_table
er2_brms_table |>
  save_tt(here(table_dir, "er2_brms_table.docx"), overwrite = TRUE)
```

### All Emotions x Gender

```{r}
f_er3 <- bf(mvbind(Anxious, Angry, Hopeful, Happy, Calm) ~ exp_condition * gender) + 
  set_rescor(FALSE)

priors_er3 <- c(
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Anxious"),
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Angry"),
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Hopeful"),
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Happy"),
  prior(normal(0.5, 0.5), class = "Intercept", resp = "Calm"),
  prior(normal(0, 0.5), class = "b", resp = "Anxious"),
  prior(normal(0, 0.5), class = "b", resp = "Angry"),
  prior(normal(0, 0.5), class = "b", resp = "Hopeful"),
  prior(normal(0, 0.5), class = "b", resp = "Happy"),
  prior(normal(0, 0.5), class = "b", resp = "Calm"),
  prior(exponential(4), class = "sigma", resp = "Anxious"),
  prior(exponential(4), class = "sigma", resp = "Angry"),
  prior(exponential(4), class = "sigma", resp = "Hopeful"),
  prior(exponential(4), class = "sigma", resp = "Happy"),
  prior(exponential(4), class = "sigma", resp = "Calm")
)
```

```{r}
#|output: false
er3 <- brm(
  data = df_mod,
  family = gaussian(),
  formula = f_er3,
  prior = priors_er3,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth
  )
)
```

```{r}
er3_brms_raw <- map(emotions, \(em) {
  tidy(er3, parameters = paste0("^b_", em), robust = TRUE, 
       conf.method = "HPDinterval", rhat = TRUE, ess = TRUE) |>
    mutate(Outcome = em,
           term = str_remove(term, paste0("b_", em, "_")))
}) |>
  list_rbind()

er3_brms <- er3_brms_raw |>
  mutate(term = case_when(
    term == "(Intercept)"                              ~ "Intercept",
    term == "exp_conditionhope"                        ~ "Hope (vs. Control)",
    term == "exp_conditionanxiety"                     ~ "Anxiety (vs. Control)",
    term == "genderfemale"                             ~ "Women (vs. Men)",
    term == "genderother"                              ~ "Other (vs. Men)",
    term == "exp_conditionhope:genderfemale"           ~ "Women x Hope",
    term == "exp_conditionanxiety:genderfemale"        ~ "Women x Anxiety",
    term == "exp_conditionhope:genderother"            ~ "Other x Hope",
    term == "exp_conditionanxiety:genderother"         ~ "Other x Anxiety",
    TRUE ~ term
  )) |>
  select(Outcome, Term = term,
         Median = estimate,
         MAD = std.error,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         "R-hat" = rhat,
         ESS = ess)
```

```{r}
er3_brms_table <- er3_brms |>
  mutate(across(where(is.numeric), \(x) round(x, 3))) |>
  select(-Outcome) |>
  tt() |>
  group_tt(i = list(
    "Anxious" = 1,
    "Angry"   = 10,
    "Hopeful" = 19,
    "Happy"   = 28,
    "Calm"    = 37
  ))

er3_brms_table
er3_brms_table |>
  save_tt(here(table_dir, "er3_brms_table.docx"), overwrite = TRUE)
```

### Predicted averages

```{r}
er1_preds <- avg_predictions(
  er1,
  by = c("group", "exp_condition")) |> 
  as_tibble() |> 
  select(Emotion = group,
         Condition = exp_condition,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         )

er1_preds |> tt()
```







