---
title: "RQ1.1 Democratic Support Models"
description: "How do feelings about the future affect young people's democratic attitudes?" 

format:
  html:
    theme: paper
    shift-heading-level-by: 1
    code-tools: true
    code-fold: true
    toc: true
    toc-fold: false
    toc-location: right
    toc-depth: 4
    toc-title: "Contents"

# Portability settings
embed-resources: true

# Execution options 
execute:
  warning: false
---

```{r}
#| include: false
# set error messages to English
Sys.setenv(LANG = "en")

knitr::opts_chunk$set(
  fig.align = "center", 
  fig.retina = 3,
  fig.width = 6, 
  fig.height = (6 * 0.618),
  out.width = "90%", 
  collapse = FALSE
)

options(
  digits = 4,
  width = 300,
  dplyr.summarise.inform = FALSE)
```

```{r}
#| include: false
#| warning: true
#| message: true
if (!require("groundhog", quietly = TRUE)) {
  install.packages("groundhog")
}
library("groundhog")

# use groundhog to install and load packages
pkgs <- c("here",         # System path management
          "tidyverse",    # ggplot, dplyr, and friends
          "datawizard",   # Data preparation tools
          "brms",         # Bayesian regression modelling in Stan
          "marginaleffects", # Model-based predictions, comparisons, and more marginalia
          "tidybayes",    # Tools to work with Bayesian models 
          "tinytable",    # Minimalist tables
          "modelsummary", # Data and model summaries with tables and plots
          "ggdist",       # Additional plot elements
          # "ggrain",       # For fancy raincloud plots
          # "GGally",       # ggpairs and other ggplot2 friends
          # "ggsignif",     # Add significance to figures
          "patchwork",    # Combine multiple ggplots
          "showtext"      # Additional fonts for plots etc
          )

groundhog.library(pkgs, "2026-01-01")
```

```{r}
#| include: false
# I use the faster cmdstanr backend for Stan in the place of rstan
# to do so install the cmdstanr package first: https://mc-stan.org/cmdstanr/
# Then run cmdstanr::install_cmdstan() to install cmdstan on your computer.
# RTools must be installed. For more info see 
# https://mc-stan.org/cmdstanr/articles/cmdstanr.html#introduction

# install.packages("cmdstanr", repos = c('https://stan-dev.r-universe.dev', getOption("repos")))
# cmdstanr::install_cmdstan()

options(mc.cores = 4,  
        brms.backend = "cmdstanr")
```

```{r}
#| include: false

showtext_auto()
showtext_opts(dpi = 600)

font_add_google("Public Sans", "Public Sans")
font_add_google("Public Sans", "Public Sans Light", regular.wt = 300)
font_add_google("Public Sans", "Public Sans Semibold", regular.wt = 600)

# Custom ggplot theme
theme_nice <- function() {
  # General text family and base size
  theme_minimal(base_family = "Public Sans", base_size = 14) +
    theme(
      # Remove minor grid lines for cleaner look
      panel.grid.minor = element_blank(),
      # Customize major grid lines color
      panel.grid.major = element_blank(),
      # Plot title: bold and custom relative size
      plot.title = element_text(family = "Public Sans", face = "bold", size = rel(1.1), margin = margin(b = 10)),
      # Subtitle and caption: lighter weight 
      plot.subtitle = element_text(family = "Public Sans Light", face = "plain"),
      plot.caption = element_text(family = "Public Sans Light", face = "plain"),
      # Axis text: Relative size
      axis.text = element_text(size = rel(0.9)),
      # Axis titles: Semibold and custom relative size
      axis.title = element_text(family = "Public Sans Semibold", size = rel(0.9)),
      axis.title.x = element_text(hjust = 0.5),
      axis.title.y = element_text(hjust = 0.5),
      # Axis lines
      axis.line = element_line(color = "grey25", linewidth = 0.8),
      # Facet labels: bold text on grey background
      strip.text = element_text(
        family = "Public Sans Semibold", face = "plain",
        size = rel(1),
        hjust = 0.5
      ),
      strip.background = element_rect(fill = "grey95", color = "grey25", linewidth = 0.8), 
      # Legend styling: compact and top-positioned
      legend.title = element_text(family = "Public Sans Semibold", size = rel(0.8)),
      legend.text = element_text(size = rel(0.8)),
      legend.position = "top",
      legend.justification = "center",
      legend.title.position = "left",
      legend.margin = margin(l = 0, t = 0)
    )
}


theme_set(theme_nice())
update_geom_defaults("text", list(family = "Public Sans"))
update_geom_defaults("label", list(family = "Public Sans"))
```

```{r}
#| include: false
data_dir <- here("01_data")
table_dir <- here("02_output", "tables", "RQ1")
figure_dir <- here("02_output", "figures", "RQ1")
model_dir <- here("02_output", "models", "RQ1")

dir.create(table_dir, recursive = TRUE, showWarnings = TRUE)
dir.create(figure_dir, recursive = TRUE, showWarnings = TRUE)
dir.create(model_dir, recursive = TRUE, showWarnings = TRUE)
```

```{r}
load(here(data_dir, "analysis", "df_wide.RData"))
df <- df_wide 
rm(df_wide)
```

## Main Models to Estimate the ATEs

```{r}
# brms settings
bayes_seed <- 42
chains <- 4
iter <- 4000
warmup <- floor(iter/2)
adapt_delta <- 0.90
max_treedepth <- 10
```

```{r}
# marginaleffects settings
options(marginaleffects_posterior_interval = "hdi")
options(marginaleffects_posterior_center = stats::median)
```

### Model 1 — Primary Model

```{r}
f_m1 <- bf(exp_dem_pomp ~ exp_condition) 

priors_m1 <- c(
  prior(normal(0.5, 0.5), class = "Intercept"),
  prior(normal(0, 0.5), class = "b"),
  prior(exponential(4), class = "sigma"))
```

```{r}
#| output: false
m1 <- brm(
  data = df,
  family = gaussian(),
  formula = f_m1,
  prior = priors_m1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "m1.rds")
  )
```

```{r}
print(m1)
```

#### Quantities of interest

```{r}
m1_pred_avg <- avg_predictions(m1) |> 
  as_tibble() |> 
  select(Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
         ) 

m1_pred_avg |> tt()
```

```{r}
m1_pred <- avg_predictions(m1, by = "exp_condition") |> 
  as_tibble() |> 
  select(Condition = exp_condition,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
         ) 

m1_pred |> tt()
```

```{r}
m1_comp <- avg_comparisons(m1, variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

m1_comp |> tt()
```

#### Frequentist comparison

```{r}
f1 <- lm(exp_dem_pomp ~ exp_condition, data = df)

f1_comp <- avg_comparisons(f1, 
                           variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Estimate = estimate,
         SE = std.error,
         `p` = p.value,
         "95% CI Lower" = conf.low,
         "95% CI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

f1_comp |> tt()
```

### Model 2 — Interaction with Age Group

```{r}
f_m2 <- bf(exp_dem_pomp ~ exp_condition * age_group) 
```

```{r}
#| output: false
m2 <- brm(
  data = df,
  family = gaussian(),
  formula = f_m2,
  prior = priors_m1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "m2.rds")
  )
```

```{r}
summary(m2)
```

#### Quantities of interest

```{r}
m2_comp <- avg_comparisons(m2, 
                           variables = list(exp_condition = "pairwise"), 
                           by = "age_group") |> 
  as_tibble() |> 
  select(Contrast = contrast,
         `Age Group` = age_group,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

m2_comp |> tt()
```

#### Frequentist comparison

```{r}
f2 <- lm(exp_dem_pomp ~ exp_condition * age_group, data = df)

f2_comp <- avg_comparisons(f2, 
                           variables = list(exp_condition = "pairwise"), 
                           by = "age_group") |> 
  as_tibble() |> 
  select(Contrast = contrast,
         `Age Group` = age_group,
         Estimate = estimate,
         SE = std.error,
         `p` = p.value,
         "95% CI Lower" = conf.low,
         "95% CI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

f2_comp |> tt()
```

### Model 3 — Interaction with Gender

```{r}
f_m3 <- bf(exp_dem_pomp ~ exp_condition * gender) 
```

```{r}
#| output: false
m3 <- brm(
  data = df,
  family = gaussian(),
  formula = f_m3,
  prior = priors_m1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "m3.rds")
)
```

```{r}
summary(m3)
```

#### Quantities of interest

```{r}
m3_comp <- avg_comparisons(m3, 
                           variables = list(exp_condition = "pairwise"), 
                           by = "gender") |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Gender = gender,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

m3_comp |> tt()
```

#### Frequentist comparison

```{r}
f3 <- lm(exp_dem_pomp ~ exp_condition * gender, data = df)

f3_comp <- avg_comparisons(f3, 
                           variables = list(exp_condition = "pairwise"), 
                           by = "gender") |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Gender = gender,
         Estimate = estimate,
         SE = std.error,
         `p` = p.value,
         "95% CI Lower" = conf.low,
         "95% CI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

f3_comp |> tt()
```

## Supplementary Models

### Model 4 — Control for Demograpics & Pre-Measures

```{r}
df_control <- df |> 
  mutate(ideology = left_right / 10,
         education_level = coalesce(education_level, education)) |> 
  droplevels()
```

```{r}
f_m4 <- bf(exp_dem_pomp ~ exp_condition + scale(age) + gender + ideology + education_level + living_standard) 
```

```{r}
#| output: false
m4 <- brm(
  data = df_control,
  family = gaussian(),
  formula = f_m4,
  prior = priors_m1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "m4.rds")
)
```

```{r}
print(m4)
```

#### Quantities of interest

```{r}
m4_comp <- avg_comparisons(m4, variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

m4_comp |> tt()
```

#### Frequentist comparison

```{r}
f4 <- lm(exp_dem_pomp ~ exp_condition + scale(age) + gender + ideology + education_level + living_standard,
         data = df_control)

f4_comp <- avg_comparisons(f4, 
                           variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Estimate = estimate,
         SE = std.error,
         `p` = p.value,
         "95% CI Lower" = conf.low,
         "95% CI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

f4_comp |> tt()
```

### Model 5 — Pre-Registered Sample Only

Participants aged 16-21 or participants who were recontacted:

```{r}
df_prereg <- df |> 
  filter(age_group == "16-21 years" | sample_type == "recontact")
```

```{r}
#| output: false
m5 <- brm(
  data = df_prereg,
  family = gaussian(),
  formula = f_m1,
  prior = priors_m1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "m5.rds")
  )
```

```{r}
summary(m5)
```

#### Quantities of interest

```{r}
m5_comp <- avg_comparisons(m5, 
                           variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

m5_comp |> tt()
```

#### Frequentist comparison

```{r}
f5 <- lm(exp_dem_pomp ~ exp_condition, data = df_prereg)

f5_comp <- avg_comparisons(f5, 
                           variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Estimate = estimate,
         SE = std.error,
         `p` = p.value,
         "95% CI Lower" = conf.low,
         "95% CI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

f5_comp |> tt()
```

### Model 6 — Attentive Participants Only 

Attentive participants:
```{r}
df_att <- df |> 
  filter(exp_attention == "Costs of living",
         pre_attention1 == "passed",
         pre_attention2 == "passed",
         pre_attention3 == "passed",
         post_attention1 == "passed")

print(paste("Excluded N =", nrow(df) - nrow(df_att), "participants who failed any single one of the pre or post attention checks."))
```

```{r}
#| output: false
m6 <- brm(
  data = df_att,
  family = gaussian(),
  formula = f_m1,
  prior = priors_m1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "m6.rds")
)
```

```{r}
summary(m6)
```

#### Quantities of interest

```{r}
m6_comp <- avg_comparisons(m6, 
                           variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

m6_comp |> tt()
```

#### Frequentist comparison

```{r}
f6 <- lm(exp_dem_pomp ~ exp_condition, data = df_att)

f6_comp <- avg_comparisons(f6, 
                           variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Estimate = estimate,
         SE = std.error,
         `p` = p.value,
         "95% CI Lower" = conf.low,
         "95% CI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

f6_comp |> tt()
```

### Model 7 — Item-level differences

```{r}
df_dem_items <- df |> 
  select(id, exp_condition, 
         exp_dem_censor_media_rev,
         exp_dem_one_party_rev,
         exp_dem_question_vote_rev,
         exp_dem_respect_elections,
         exp_dem_ignore_courts_rev,
         exp_dem_ignore_parliament_rev,
         exp_dem_bend_law_rev) |> 
  pivot_longer(
    cols = exp_dem_censor_media_rev:exp_dem_bend_law_rev,
    names_to = "item",
    values_to = "response"
  ) |> 
  mutate(
    response_pomp = (response - 1) / (5 - 1),  # Convert 1-5 to 0-1
    item = factor(item, 
                  levels = c("exp_dem_censor_media_rev",
                            "exp_dem_one_party_rev",
                            "exp_dem_question_vote_rev",
                            "exp_dem_respect_elections",
                            "exp_dem_ignore_courts_rev",
                            "exp_dem_ignore_parliament_rev",
                            "exp_dem_bend_law_rev"),
                  labels = c("FreeExp", "FreeAssc", "UniSuff", 
                            "FFElect", "JudCnstr", "LegCnstr", "EqLaw"))
  )
```

```{r}
f_m7 <- bf(response_pomp ~ exp_condition * item + (1 | id))

priors_m7 <- c(
  prior(normal(0.5, 0.5), class = "Intercept"),
  prior(normal(0, 0.5), class = "b"),
  prior(exponential(4), class = "sigma"),
  prior(exponential(2), class = "sd")
)
```

```{r}
#| output: false
m7 <- brm(
  data = df_dem_items,
  family = gaussian(),
  formula = f_m7,
  prior = priors_m7,
  # sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth
  ),
  file = here(model_dir, "m7.rds")
)
```

#### Quantities of interest

```{r}
# Get posterior predictions 
m7.draws <- expand.grid(
  exp_condition = c("control", "anxiety", "hope"),
  item = levels(df_dem_items$item)) |>
  add_epred_draws(m7, re_formula = NA, ndraws = 4000) |>
  ungroup()

# Compute item-level pairwise contrasts 
m7.item_contrasts <- m7.draws |>
  select(exp_condition, item, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Anxiety - Hope` = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(type = "Item-level")

# Compute pairwise comparisons across items
m7.avg_contrasts <- m7.item_contrasts |>
  group_by(contrast, .draw) |>
  summarise(estimate = mean(estimate), .groups = "drop") |>
  mutate(
    item = "Overall ATE",
    type = "Overall"
  )

# Combine draws
m7.contrasts <- bind_rows(m7.item_contrasts, m7.avg_contrasts) |>
  mutate(
    item = factor(item, levels = c(levels(df_dem_items$item), "Overall ATE")),
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety − Control", "Hope − Control"))
  )

# Compute whether HDI excludes zero for each item
m7.hdi_check <- m7.contrasts |>
  mutate(estimate = estimate * 100) |>
  group_by(item, contrast) |>
  median_hdi(estimate, .width = 0.95) |>
  mutate(excludes_zero = if_else(sign(.lower) == sign(.upper), "Excludes zero", "Includes zero")) |>
  select(item, contrast, excludes_zero)
```

```{r}
#| fig-height: 5
#| fig-width: 10
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)
m7.contrasts |>
  mutate(estimate = estimate * 100) |>
  left_join(m7.hdi_check, by = c("item", "contrast")) |>
  ggplot(aes(x = estimate, y = item, fill = excludes_zero)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  stat_slabinterval(
    .width = c(.95),
    point_interval = "median_hdi",
    scale = 0.7,
    slab_alpha = 0.6,        
    interval_alpha = 1,      
    point_alpha = 1,          
    normalize = "groups",
    point_size = 2.5,
    interval_size = 1.5) +
  facet_wrap(~contrast) +
  scale_fill_manual(
    name = "95% HDI",
    values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
  ) +
  # scale_color_manual(
  #   name = "95% HDI",
  #   values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
  # ) +
  scale_x_continuous(limits = c(-15, 15), breaks = seq(-10, 10, by = 5), expand = expansion(add = 2.5)) +
  labs(
    x = "Percentage Points",
    y = NULL,
    title = "Treatment Effects on Democratic Support",
    subtitle = "Posterior Distributions with Median and 95% HDI"
  ) +
  theme_nice() +
  theme(
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2),
    legend.position = "bottom"
  )

ggsave(here(figure_dir, "dem_mod_item.png"),
       height = 5,
       width = 10,
       dpi = 600)
```

```{r}
m7.ate_table <- m7.contrasts |>
  filter(type == "Item-level") |>  
  group_by(contrast, .draw) |>
  summarise(estimate = mean(estimate), .groups = "drop") |>
  group_by(contrast) |>
  median_hdi(estimate, .width = 0.95) |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = .lower,
         "95% HDI Upper" = .upper
  ) 

m7.ate_table |> 
  tt()
```

```{r}
m7.cate_table <- m7.contrasts |>
  filter(type == "Item-level") |>
  group_by(contrast, item) |>
  median_hdi(estimate, .width = 0.95) |> 
  select(Contrast = contrast,
         Item = item,
         Median = estimate,
         "95% HDI Lower" = .lower,
         "95% HDI Upper" = .upper
  ) 

m7.cate_table |> 
  tt()
```

## Visualize Models 1, 2, 5

### Extract Posterior Draws

```{r}
# M1: Overall ATE
m1.draws <- expand.grid(
  exp_condition = c("control", "anxiety", "hope")
) |>
  add_epred_draws(m1, re_formula = NA, ndraws = 4000) |>
  ungroup()

m1.contrasts <- m1.draws |>
  select(exp_condition, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Anxiety - Hope` = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(
    model = "ATE",
    subgroup = "ATE"
  )

# M2: cATE by age_group
m2.draws <- expand.grid(
  exp_condition = c("control", "anxiety", "hope"),
  age_group = unique(df$age_group)
  ) |>
  add_epred_draws(m2, re_formula = NA, ndraws = 4000) |>
  ungroup()

m2.contrasts <- m2.draws |>
  select(exp_condition, age_group, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Anxiety - Hope` = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(
    model = "Age",
    subgroup = as.character(age_group)
  ) |>
  select(-age_group)

# m3: cATE by gender
m3.draws <- expand.grid(
  exp_condition = c("control", "anxiety", "hope"),
  gender = unique(df$gender)
) |>
  add_epred_draws(m3, re_formula = NA, ndraws = 4000) |>
  ungroup() |> 
  filter(gender != "other")

m3.contrasts <- m3.draws |>
  select(exp_condition, gender, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Anxiety - Hope` = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(
    model = "Gender",
    subgroup = as.character(gender)
  ) |>
  select(-gender)

pairwise_plot_data <- bind_rows(m1.contrasts, m2.contrasts, m3.contrasts) |>
  mutate(
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety − Control", "Hope − Control")),
    model = factor(model, levels = c("ATE", "Age", "Gender"))
  )

# Compute whether HDI excludes zero for each group
hdi_check <- pairwise_plot_data |>
  mutate(
    estimate = estimate * 100,
    subgroup = case_when(
      subgroup == "male" ~ "Men",
      subgroup == "female" ~ "Women",
      subgroup == "16-21 years" ~ "16-21",
      subgroup == "22-26 years" ~ "22-26",
      TRUE ~ subgroup
    ),
    subgroup = factor(subgroup, levels = c("ATE", "22-26", "16-21", "Women", "Men"))
  ) |>
  group_by(model, contrast, subgroup) |>
  median_hdi(estimate, .width = 0.95) |>
  mutate(excludes_zero = if_else(sign(.lower) == sign(.upper), "Excludes zero", "Includes zero")) |>
  select(model, contrast, subgroup, excludes_zero)
```

### Visualize

```{r}
#| fig-height: 5.5
#| fig-width: 8
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)

pairwise_plot_data |>
  mutate(
    estimate = estimate * 100,
    subgroup = case_when(
      subgroup == "male" ~ "Men",
      subgroup == "female" ~ "Women",
      subgroup == "16-21 years" ~ "16-21",
      subgroup == "22-26 years" ~ "22-26",
      TRUE ~ subgroup
    ),
    subgroup = factor(subgroup, levels = c("ATE", "22-26", "16-21", "Women", "Men"))
  ) |>
  left_join(hdi_check, by = c("model", "contrast", "subgroup")) |>
  ggplot(aes(x = estimate, y = subgroup, fill = excludes_zero)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  stat_slabinterval(
    .width = c(.95),
    point_interval = "median_hdi",
    scale = 0.7,
    slab_alpha = 0.6,        
    interval_alpha = 1,      
    point_alpha = 1,          
    normalize = "groups",
    point_size = 2.5,
    interval_size = 1.5) +
  facet_grid(model ~ contrast, scales = "free_y", space = "free_y") +
  scale_fill_manual(
    values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
    name = "95% HDI",
  ) +
  # scale_color_manual(
  #   values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
  #   name = "95% HDI",
  # ) +
  scale_x_continuous(limits = c(-10, 10), breaks = seq(-10, 10, by = 5), expand = expansion(add = 2.5)) +
  labs(
    x = "Percentage Points",
    y = NULL,
    title = "Effects on Democratic Support",
    subtitle = "Posterior Distributions with Median and 95% HDI"
  ) +
  theme_nice() +
  theme(
    legend.position = "bottom",
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2)
  ) 

ggsave(here(figure_dir, "RQ1.1_ate_cate_posterior.png"),
       height = 5.5,
       width = 8,
       dpi = 600)
```







