---
title: "RQ1.2 Democratic Candidate Choice Models"
description: "How do feelings about the future affect young people's democratic candidate choices?" 

format:
  html:
    theme: paper
    shift-heading-level-by: 1
    code-tools: true
    code-fold: true
    toc: true
    toc-fold: false
    toc-location: right
    toc-depth: 4
    toc-title: "Contents"

# Portability settings
embed-resources: true

# Execution options 
execute:
  warning: false
---

```{r}
#| include: false
# set error messages to English
Sys.setenv(LANG = "en")

knitr::opts_chunk$set(
  fig.align = "center", 
  fig.retina = 3,
  fig.width = 6, 
  fig.height = (6 * 0.618),
  out.width = "90%", 
  collapse = FALSE
)

options(
  digits = 4,
  width = 300,
  dplyr.summarise.inform = FALSE)
```

```{r}
#| include: false
#| warning: true
#| message: true
if (!require("groundhog", quietly = TRUE)) {
  install.packages("groundhog")
}
library("groundhog")

# use groundhog to install and load packages
pkgs <- c("here",         # System path management
          "tidyverse",    # ggplot, dplyr, and friends
          "datawizard",   # Data preparation tools
          "brms",         # Bayesian regression modelling in Stan
          "cregg",        # Frequentist conjoint analysis
          "marginaleffects", # Model-based predictions, comparisons, and more marginalia
          "tidybayes",    # Tools to work with Bayesian models 
          "tinytable",    # Minimalist tables
          "modelsummary", # Data and model summaries with tables and plots
          "ggdist",       # Additional plot elements
          # "ggrain",       # For fancy raincloud plots
          # "GGally",       # ggpairs and other ggplot2 friends
          # "ggsignif",     # Add significance to figures
          "ggforce",         # extension to ggplot
          "patchwork",    # Combine multiple ggplots
          "showtext"      # Additional fonts for plots etc
          )

groundhog.library(pkgs, "2026-01-01")
```

```{r}
#| include: false
# I use the faster cmdstanr backend for Stan in the place of rstan
# to do so install the cmdstanr package first: https://mc-stan.org/cmdstanr/
# Then run cmdstanr::install_cmdstan() to install cmdstan on your computer.
# RTools must be installed. For more info see 
# https://mc-stan.org/cmdstanr/articles/cmdstanr.html#introduction

# install.packages("cmdstanr", repos = c('https://stan-dev.r-universe.dev', getOption("repos")))
# cmdstanr::install_cmdstan()

options(mc.cores = 4,  
        brms.backend = "cmdstanr")
```

```{r}
#| include: false

showtext_auto()
showtext_opts(dpi = 600)

font_add_google("Public Sans", "Public Sans")
font_add_google("Public Sans", "Public Sans Light", regular.wt = 300)
font_add_google("Public Sans", "Public Sans Semibold", regular.wt = 600)

# Custom ggplot theme
theme_nice <- function() {
  # General text family and base size
  theme_minimal(base_family = "Public Sans", base_size = 14) +
    theme(
      # Remove minor grid lines for cleaner look
      panel.grid.minor = element_blank(),
      # Customize major grid lines color
      panel.grid.major = element_blank(),
      # Plot title: bold and custom relative size
      plot.title = element_text(family = "Public Sans", face = "bold", size = rel(1.1), margin = margin(b = 10)),
      # Subtitle and caption: lighter weight 
      plot.subtitle = element_text(family = "Public Sans Light", face = "plain"),
      plot.caption = element_text(family = "Public Sans Light", face = "plain"),
      # Axis text: Relative size
      axis.text = element_text(size = rel(0.9)),
      # Axis titles: Semibold and custom relative size
      axis.title = element_text(family = "Public Sans Semibold", size = rel(0.9)),
      axis.title.x = element_text(hjust = 0.5),
      axis.title.y = element_text(hjust = 0.5),
      # Axis lines
      axis.line = element_line(color = "grey25", linewidth = 0.8),
      # Facet labels: bold text on grey background
      strip.text = element_text(
        family = "Public Sans Semibold", face = "plain",
        size = rel(1),
        hjust = 0.5
      ),
      strip.background = element_rect(fill = "grey95", color = "grey25", linewidth = 0.8), 
      # Legend styling: compact and top-positioned
      legend.title = element_text(family = "Public Sans Semibold", size = rel(0.8)),
      legend.text = element_text(size = rel(0.8)),
      legend.position = "top",
      legend.justification = "center",
      legend.title.position = "left",
      legend.margin = margin(l = 0, t = 0)
    )
}


theme_set(theme_nice())
update_geom_defaults("text", list(family = "Public Sans"))
update_geom_defaults("label", list(family = "Public Sans"))
```

```{r}
#| include: false
data_dir <- here("01_data")
table_dir <- here("02_output", "tables", "RQ1")
figure_dir <- here("02_output", "figures", "RQ1")
model_dir <- here("02_output", "models", "RQ1")

dir.create(table_dir, recursive = TRUE, showWarnings = TRUE)
dir.create(figure_dir, recursive = TRUE, showWarnings = TRUE)
dir.create(model_dir, recursive = TRUE, showWarnings = TRUE)
```

```{r}
load(here(data_dir, "analysis", "df_long.RData"))

df_long <- df_long |> 
  mutate(conjoint_choice = as.numeric(conjoint_choice),
         conjoint_sex = factor(conjoint_sex, levels = c("Male", "Female")),
         conjoint_age = as.numeric(conjoint_age),
         conjoint_party = factor(conjoint_party, 
                                 levels = c("Labour", "Conservatives", "Liberal Democrats", 
                                            "Green Party", "Reform UK")),
         conjoint_dem = factor(conjoint_dem, 
                     levels = c("undemocratic", "democratic"),
                     labels = c("Undemocratic", "Democratic")),
         conjoint_eco = factor(conjoint_eco, 
                     levels = c("Neither good nor bad reputation on economic matters",
                                "Good at handling economic matters",
                                "Bad at handling economic matters"),
                     labels = c("Neither", "Economically good", "Economically bad"))) |> 
  mutate(conjoint_age_z = standardise(conjoint_age))

levels(df_long$conjoint_sex)
levels(df_long$conjoint_party)
levels(df_long$conjoint_dem)
levels(df_long$conjoint_eco)

# Variable lookup table for later
variable_lookup <- tibble(
  variable = c("conjoint_sex", "conjoint_age_z", "conjoint_party", "conjoint_dem", "conjoint_eco"),
  variable_nice = c("Sex", "Age", "Party", "Democratic behaviour", "Economic reputation")
)
```

```{r}
# brms settings
bayes_seed <- 42
chains <- 4
iter <- 4000
warmup <- floor(iter/2)
adapt_delta <- 0.90
max_treedepth <- 10
```

```{r}
# marginaleffects settings
options(marginaleffects_posterior_interval = "hdi")
options(marginaleffects_posterior_center = stats::median)
```

## Model 0 — Conjoint Choices

```{r}
f_cj0 <- bf(conjoint_choice ~ conjoint_dem + conjoint_sex + conjoint_age_z + conjoint_party + conjoint_eco + (1 | id))

priors_cj0 <- c(
  prior(normal(0, 1), class = "Intercept"),
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sd")
)
```

```{r}
#| output: false
cj0 <- brm(
  data = df_long,
  family = bernoulli(link = "logit"),
  formula = f_cj0,
  prior = priors_cj0,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "cj0.rds")
)
```

```{r}
print(cj0)
```

#### Quantities of interest

Thanks go to Andrew Heiss and his [amazing blog](https://www.andrewheiss.com/blog/2023/07/25/conjoint-bayesian-frequentist-guide/#finding-conjoint-amces-and-marginal-means-bayesianly) from where I borrow much of this code!

##### Average Marginal Component Effects (AMCEs) 

```{r}
cj0_slopes <- avg_slopes(cj0, 
                         newdata = datagrid(id = unique(df_long$id))) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(Contrast = if_else(Contrast == "dY/dX", "Age (1 SD increase)", Contrast),
         across(where(is.numeric), \(x) round(x, 3))) 

cj0_slopes |> tt()

cj0_slopes |> tt() |> 
  save_tt(here(table_dir, "conjoint_amces.docx"), overwrite = TRUE)
```

```{r}
# Create levels for all variables 
cj0_levels <- tibble(
  variable = c("conjoint_sex", "conjoint_age_z", "conjoint_party", "conjoint_dem", "conjoint_eco"),
  levels = "") |> 
  mutate(levels = case_when(
    variable == "conjoint_sex" ~ list(levels(df_long$conjoint_sex)),
    variable == "conjoint_age_z" ~ list("1 SD increase"),
    variable == "conjoint_party" ~ list(levels(df_long$conjoint_party)),
    variable == "conjoint_dem" ~ list(levels(df_long$conjoint_dem)),
    variable == "conjoint_eco" ~ list(levels(df_long$conjoint_eco))
  )) |> 
  unnest(levels) |>
  mutate(term = paste0(variable, levels))

# Calculate Average Marginal Effects and get Posterior Draws
cj0_mfx <- cj0 |>
  avg_slopes(newdata = datagrid(id = unique(df_long$id))) |>  
  posterior_draws() 

# Reshape Results (handle continuous and categorical separately)
cj0_mfx_nested <- cj0_mfx |>
  mutate(
    variable_level = if_else(
      term == "conjoint_age_z",
      "1 SD increase",
      str_extract(contrast, "^[^-]+(?= - )")
    )
  ) |>
  group_by(term, variable_level) |>
  nest()

# Join Data
cj0_plot_data <- cj0_levels |>
  left_join(
    cj0_mfx_nested,
    by = join_by(variable == term, levels == variable_level)
  ) |>
  mutate(data = map_if(data, is.null, ~ tibble(draw = 0, estimate = 0))) |>
  unnest(data) |>
  left_join(variable_lookup, by = join_by(variable)) |>
  mutate(across(c(levels, variable_nice), ~fct_inorder(.)))
```

```{r}
#| fig-height: 7
#| fig-width: 8
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)

cj0_plot_data |> 
  
  ggplot(aes(x = draw, y = levels, fill = variable_nice, color = variable_nice)) +
  
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  
  stat_slab(
    data = ~filter(.x, draw != 0),
    aes(thickness = after_stat(pdf)),
    scale = 0.7,
    alpha = 0.7,
    normalize = "groups"
  ) +
  
  stat_pointinterval(
    .width = c(.95),
    point_interval = "median_hdi",
    position = position_nudge(y = -0.1),
    point_size = 2,
  ) +
  
  facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
  
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  
  scale_x_continuous(
    labels = scales::percent, 
    limits = c(-0.5, 0.5), 
    breaks = seq(-0.5, 0.5, by = 0.1),
    expand = expansion(add = 0.025)
  ) +
  
  labs(
    x = "Probability Change to Choose Candidate (vs. Reference)", 
    y = NULL,  
    title = "Average Marginal Component Effects",
    subtitle = "Posterior Distributions with Median and 95% HDI"
  ) +
  
  theme_nice() +
  theme(
    legend.position = "none",
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2)
  )

ggsave(here(figure_dir, "conjoint_amce.png"),
       height = 7,
       width = 8,
       dpi = 600)
```

##### Marginal Means

```{r}
cj0_mm_sex <- avg_predictions(cj0, by = "conjoint_sex") |> as_tibble()
cj0_mm_party <- avg_predictions(cj0, by = "conjoint_party") |> as_tibble()
cj0_mm_dem <- avg_predictions(cj0, by = "conjoint_dem") |> as_tibble()
cj0_mm_eco <- avg_predictions(cj0, by = "conjoint_eco") |> as_tibble()
cj0_mm_age <- avg_predictions(cj0, 
                              newdata = datagrid(conjoint_age_z = c(-1, 0, 1)),
                              by = "conjoint_age_z") |> as_tibble()

cj0_mm <- bind_rows(cj0_mm_sex, cj0_mm_party, cj0_mm_dem, cj0_mm_eco, cj0_mm_age)
```

```{r}
cj0_mm_table <- cj0_mm |> 
  pivot_longer(
    cols = starts_with("conjoint_"), 
    names_to = "Attribute", 
    values_to = "Level", 
    values_transform = as.character, 
    values_drop_na = TRUE
  ) |> 
  mutate(
    # Clean the Attribute names 
    Attribute = Attribute |> 
      str_remove("conjoint_") |> 
      str_remove("_z") |>       # Removes "_z" from age
      str_to_title(),           # Capitalizes the first letter
    
    # Recode the Age Levels
    Level = case_when(
      Attribute == "Age" & Level == "-1" ~ "-1 SD",
      Attribute == "Age" & Level == "0"  ~ "Mean",
      Attribute == "Age" & Level == "1"  ~ "+1 SD",
      TRUE ~ Level 
    )
  ) |> 
  # Final Selection and Formatting
  select(
    Attribute, 
    Level,
    Median = estimate,
    "95% HDI Lower" = conf.low,
    "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

cj0_mm_table |> tt()
```

## Model 1 — Primary Model

```{r}
f_cj1 <- bf(conjoint_choice ~ conjoint_dem * exp_condition + conjoint_sex + conjoint_age_z + conjoint_party + conjoint_eco + (1 | id))

priors_cj1 <- c(
  prior(normal(0, 1), class = "Intercept"),
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sd")
)
```

```{r}
#| output: false
cj1 <- brm(
  data = df_long,
  family = bernoulli(link = "logit"),
  formula = f_cj1,
  prior = priors_cj1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "cj1.rds")
)
```

```{r}
print(cj1)
```

### Quantities of Interest

#### Average Comparisons

```{r}
cj1_main_com <- avg_comparisons(cj1, 
                                variables = list("conjoint_dem" = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3))) 

cj1_main_com |> tt()
```


```{r}
cj1_com <- avg_comparisons(cj1, 
                           variables = list("conjoint_dem" = "pairwise"), 
                           by = "exp_condition") |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Condition = exp_condition,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3))) 

cj1_com |> tt()
```

```{r}
cj1_hyp <- avg_comparisons(cj1, 
                           variables = list("conjoint_dem" = "pairwise"), 
                           by = "exp_condition", 
                           hypothesis = ~pairwise) |> 
  as_tibble() |> 
  select(Hypothesis = hypothesis,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3))) 

cj1_hyp |> tt()
```

#### Conditional Marginal Means

```{r}
cj1_mms <- predictions(
  cj1,
  by = c("conjoint_dem", "exp_condition"),
  allow_new_levels = TRUE) |> 
  posterior_draws()

cj1_mms |> 
  group_by(conjoint_dem, exp_condition) %>% 
  median_qi(draw) |> 
  tt()
```

## Model 2 — Interaction with Age 

```{r}
f_cj2 <- bf(conjoint_choice ~ conjoint_dem * exp_condition * age_group + conjoint_sex + conjoint_age_z + conjoint_party + conjoint_eco + (1 | id))
```

```{r}
#| output: false
cj2 <- brm(
  data = df_long,
  family = bernoulli(link = "logit"),
  formula = f_cj2,
  prior = priors_cj1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "cj2.rds")
)
```

```{r}
print(cj2)
```

## Model 3 — Interaction with Gender

```{r}
f_cj3 <- bf(conjoint_choice ~ conjoint_dem * exp_condition * gender + conjoint_sex + conjoint_age_z + conjoint_party + conjoint_eco + (1 | id))
```

```{r}
#| output: false
cj3 <- brm(
  data = df_long,
  family = bernoulli(link = "logit"),
  formula = f_cj3,
  prior = priors_cj1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "cj3.rds")
)
```

```{r}
print(cj3)
```

## Visualization

### Get Posterior Draws

```{r}
# CJ1: Overall cAMCEs by experimental condition
cj1.cAMCEs <- cj1 |>
  avg_slopes(
    variables = "conjoint_dem",
    by = "exp_condition",
    re_formula = NA
  ) |>
  posterior_draws()

# Compute pairwise contrasts 
cj1.contrasts <- cj1.cAMCEs |>
  select(drawid, exp_condition, draw) |>  
  pivot_wider(names_from = exp_condition, values_from = draw) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Hope − Anxiety` = hope - anxiety
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Hope − Anxiety`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(
    model = "ATE",
    subgroup = "ATE"
  )

cj1.contrasts |>
  group_by(contrast, model, subgroup) |>
  median_hdi(estimate, .width = 0.95) |> tt()
```

```{r}
# CJ3: cAMCEs by condition × age group
cj2.cAMCEs <- cj2 |>
  avg_slopes(
    variables = "conjoint_dem",
    by = c("exp_condition", "age_group"),
    re_formula = NA
  ) |>
  posterior_draws()

# Compute pairwise contrasts within each age group
cj2.contrasts <- cj2.cAMCEs |>
  select(drawid, exp_condition, age_group, draw) |>
  pivot_wider(names_from = exp_condition, values_from = draw) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Hope − Anxiety` = hope - anxiety
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Hope − Anxiety`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(
    model = "Age",
    subgroup = as.character(age_group)
  ) |>
  select(-age_group)

cj2.contrasts |>
  group_by(contrast, model, subgroup) |>
  median_hdi(estimate, .width = 0.95) |> tt()
```

```{r}
# CJ4: cAMCEs by condition × gender
cj3.cAMCEs <- cj3 |>
  avg_slopes(
    variables = "conjoint_dem",
    by = c("exp_condition", "gender"),
    re_formula = NA
  ) |>
  posterior_draws()

# Compute pairwise contrasts within each gender
cj3.contrasts <- cj3.cAMCEs |>
  select(drawid, exp_condition, gender, draw) |>
  pivot_wider(names_from = exp_condition, values_from = draw) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Hope − Anxiety` = hope - anxiety
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Hope − Anxiety`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(
    model = "Gender",
    subgroup = as.character(gender)
  ) |>
  select(-gender)

cj3.contrasts |>
  group_by(contrast, model, subgroup) |>
  median_hdi(estimate, .width = 0.95) |> tt()
```

```{r}
# Combine all contrasts
cj_pairwise_plot_data <- bind_rows(cj1.contrasts, cj2.contrasts, cj3.contrasts) |>
  filter(subgroup != "other") |> 
  mutate(
    # Relabel gender
    subgroup = case_when(
      subgroup == "male" ~ "Men",
      subgroup == "female" ~ "Women",
      subgroup == "16-21 years" ~ "16-21",
      subgroup == "22-26 years" ~ "22-26",
      TRUE ~ subgroup
    ),
    # Set factor levels
    contrast = factor(contrast, levels = c("Anxiety − Control", "Hope − Control", "Hope − Anxiety")),
    model = factor(model, levels = c("ATE", "Age", "Gender")),
    subgroup = factor(subgroup, levels = c("ATE", "22-26", "16-21", "Women", "Men"))
  )

# Compute whether HDI excludes zero for each group
cj_hdi_check <- cj_pairwise_plot_data |>
  group_by(model, contrast, subgroup) |>
  median_hdi(estimate, .width = 0.95) |>
  mutate(excludes_zero = if_else(sign(.lower) == sign(.upper), "Excludes zero", "Includes zero")) |>
  select(model, contrast, subgroup, excludes_zero)
```

### Create Figure

```{r}
#| fig-height: 5.5
#| fig-width: 8
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)
cj_pairwise_plot_data |>
  mutate(estimate = estimate * 100) |>
  left_join(cj_hdi_check, by = c("model", "contrast", "subgroup")) |>
  ggplot(aes(x = estimate, y = subgroup, fill = excludes_zero)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  stat_slabinterval(
    .width = c(.95),
    point_interval = "median_hdi",
    scale = 0.7,
    slab_alpha = 0.6,        
    interval_alpha = 1,      
    point_alpha = 1,          
    normalize = "groups",
    point_size = 2.5,
    interval_size = 1.5) +
  facet_grid(model ~ contrast, scales = "free_y", space = "free_y") +
  scale_fill_manual(
    values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
    name = "95% HDI",
  ) +
  # scale_color_manual(
  #   values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
  #   name = "95% HDI",
  # ) +
  scale_x_continuous(limits = c(-20, 20), breaks = seq(-15, 15, by = 5), expand = expansion(add = 0.5)) +
  labs(
    x = "Percentage Points",
    y = NULL,
    title = "Effects on Democratic Candidate Preference",
    subtitle = "Positive Differences = Preference for Democratic Candidates"
  ) +
  theme_nice() +
  theme(
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2),
    legend.position = "none"
  )

ggsave(here(figure_dir, "RQ1.2_ate_cate_posterior.png"),
       height = 5.5,
       width = 8,
       dpi = 600)
```

## Model 4 — Control for Demograpics & Pre-Measures

```{r}
df_control <- df_long |> 
  mutate(ideology = left_right / 10,
         education_level = coalesce(education_level, education)) |> 
  droplevels()
```

```{r}
f_cj4 <- bf(conjoint_choice ~ conjoint_dem * exp_condition + conjoint_sex + conjoint_age_z + conjoint_party + conjoint_eco + scale(participant_age) + gender + ideology + education_level + living_standard + (1 | id))

priors_cj4 <- c(
  prior(normal(0, 1), class = "Intercept"),
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sd")
)
```

```{r}
#| output: false
cj4 <- brm(
  data = df_control,
  family = bernoulli(link = "logit"),
  formula = f_cj4,
  prior = priors_cj4,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "cj4.rds")
)
```

```{r}
print(cj4)
```

## Model 5 — Pre-Registered Sample Only

Participants aged 16-21 or participants who were recontacted:

```{r}
df_prereg <- df_long |> 
  filter(age_group == "16-21 years" | sample_type == "recontact")
```

```{r}
f_cj5 <- bf(conjoint_choice ~ conjoint_dem * exp_condition + conjoint_sex + conjoint_age_z + conjoint_party + conjoint_eco + (1 | id))

priors_cj5 <- c(
  prior(normal(0, 1), class = "Intercept"),
  prior(normal(0, 1), class = "b"),
  prior(exponential(1), class = "sd")
)
```

```{r}
#| output: false
cj5 <- brm(
  data = df_prereg,
  family = bernoulli(link = "logit"),
  formula = f_cj5,
  prior = priors_cj5,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "cj5.rds")
)
```

```{r}
print(cj5)
```

## Supplementary Models

## Eco Model — Trading Off Democracy for Ecomony?

```{r}
f_cj_eco <- bf(conjoint_choice ~ conjoint_dem * conjoint_eco + conjoint_sex + conjoint_age_z + conjoint_party + (1 | id))
```

```{r}
#| output: false
cj_eco <- brm(
  data = df_long,
  family = bernoulli(link = "logit"),
  formula = f_cj_eco,
  prior = priors_cj0,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth),
  file = here(model_dir, "cj_eco.rds")
)
```

```{r}
print(cj_eco)
```

### Quantities of Interest

```{r}
cj_eco_pred <- plot_predictions(cj_eco, by = c("conjoint_dem", "conjoint_eco"), draw = F)
```

```{r}
cj_eco_pred |> 
  ggplot(aes(x = conjoint_dem, y = estimate, color = conjoint_eco)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high),
                  position = position_dodge(width = 0.2),
                  size = 0.5, linewidth = 1) +
  scale_y_continuous(
    limits = c(0.1, 0.9), 
    breaks = seq(0, 1, by = 0.2),
    labels = scales::percent  
  ) +
  labs(
    x = "Recent behaviour",
    y = "Marginal mean",
    title = "Marginal means",
    color = "Economic reputation" 
  ) 
```











