---
title: "RQ2.1 Political Information Seeking Models"
description: "How do feelings about the future affect young people's political information seeking?" 

format:
  html:
    theme: paper
    shift-heading-level-by: 1
    code-tools: true
    code-fold: true
    toc: true
    toc-fold: false
    toc-location: right
    toc-depth: 4
    toc-title: "Contents"

# Portability settings
embed-resources: true

# Execution options 
execute:
  warning: false
---

```{r}
#| include: false
# set error messages to English
Sys.setenv(LANG = "en")

knitr::opts_chunk$set(
  fig.align = "center", 
  fig.retina = 3,
  fig.width = 6, 
  fig.height = (6 * 0.618),
  out.width = "90%", 
  collapse = FALSE
)

options(
  digits = 4,
  width = 300,
  dplyr.summarise.inform = FALSE)
```

```{r libraries, warning=T, message=T}
#| include: false
#| warning: true
#| message: true
if (!require("groundhog", quietly = TRUE)) {
  install.packages("groundhog")
}
library("groundhog")

# use groundhog to install and load packages
pkgs <- c("here",         # System path management
          "tidyverse",    # ggplot, dplyr, and friends
          "datawizard",   # Data preparation tools
          "performance",  # Outlier, indices of model quality, and goodness of fit
          "brms",         # Bayesian regression modelling in Stan
          "marginaleffects", # Model-based predictions, comparisons, and more marginalia
          "tidybayes",    # Tools to work with Bayesian models 
          "tinytable",    # Minimalist tables
          "modelsummary", # Data and model summaries with tables and plots
          "ggdist",       # Additional plot elements
          "ggrain",       # For fancy raincloud plots
          # "GGally",       # ggpairs and other ggplot2 friends
          # "ggsignif",     # Add significance to figures
          "patchwork",    # Combine multiple ggplots
          "showtext"      # Additional fonts for plots etc
          )

groundhog.library(pkgs, "2026-01-01")
```

```{r}
#| include: false
# I use the faster cmdstanr backend for Stan in the place of rstan
# to do so install the cmdstanr package first: https://mc-stan.org/cmdstanr/
# Then run cmdstanr::install_cmdstan() to install cmdstan on your computer.
# RTools must be installed. For more info see 
# https://mc-stan.org/cmdstanr/articles/cmdstanr.html#introduction

# install.packages("cmdstanr", repos = c('https://stan-dev.r-universe.dev', getOption("repos")))
# cmdstanr::install_cmdstan()

options(mc.cores = 4,  
        brms.backend = "cmdstanr")
```

```{r}
#| include: false

showtext_auto()
showtext_opts(dpi = 600)

font_add_google("Public Sans", "Public Sans")
font_add_google("Public Sans", "Public Sans Light", regular.wt = 300)
font_add_google("Public Sans", "Public Sans Semibold", regular.wt = 600)

# Custom ggplot theme
theme_nice <- function() {
  # General text family and base size
  theme_minimal(base_family = "Public Sans", base_size = 14) +
    theme(
      # Remove minor grid lines for cleaner look
      panel.grid.minor = element_blank(),
      # Customize major grid lines color
      panel.grid.major = element_blank(),
      # Plot title: bold and custom relative size
      plot.title = element_text(family = "Public Sans", face = "bold", size = rel(1.1), margin = margin(b = 10)),
      # Subtitle and caption: lighter weight 
      plot.subtitle = element_text(family = "Public Sans Light", face = "plain"),
      plot.caption = element_text(family = "Public Sans Light", face = "plain"),
      # Axis text: Relative size
      axis.text = element_text(size = rel(0.9)),
      # Axis titles: Semibold and custom relative size
      axis.title = element_text(family = "Public Sans Semibold", size = rel(0.9)),
      axis.title.x = element_text(hjust = 0.5),
      axis.title.y = element_text(hjust = 0.5),
      # Axis lines
      axis.line = element_line(color = "grey25", linewidth = 0.8),
      # Facet labels: bold text on grey background
      strip.text = element_text(
        family = "Public Sans Semibold", face = "plain",
        size = rel(1),
        hjust = 0.5
      ),
      strip.background = element_rect(fill = "grey95", color = "grey25", linewidth = 0.8), 
      # Legend styling: compact and top-positioned
      legend.title = element_text(family = "Public Sans Semibold", size = rel(0.8)),
      legend.text = element_text(size = rel(0.8)),
      legend.position = "top",
      legend.justification = "center",
      legend.title.position = "left",
      legend.margin = margin(l = 0, t = 0)
    )
}


theme_set(theme_nice())
update_geom_defaults("text", list(family = "Public Sans"))
update_geom_defaults("label", list(family = "Public Sans"))
```

```{r}
#| include: false
data_dir <- here("01_data")
table_dir <- here("02_output", "tables", "RQ2")
figure_dir <- here("02_output", "figures", "RQ2")
model_dir <- here("02_output", "models", "RQ2")

dir.create(table_dir, recursive = TRUE, showWarnings = TRUE)
dir.create(figure_dir, recursive = TRUE, showWarnings = TRUE)
dir.create(model_dir, recursive = TRUE, showWarnings = TRUE)
```

```{r}
load(here(data_dir, "analysis", "df_wide.RData"))
df <- df_wide
rm(df_wide)
```

## Quick Look at Data

```{r}
df |> 
  mutate(
    exp_polinfo = factor(exp_polinfo,
                         levels = c("No, I do not want to see information on how to get more involved in democracy",
                                    "Yes, I want to see information on how to get more involved in democracy"),
                         labels = c("No", "Yes"))) |> 
  datasummary_crosstab(exp_polinfo ~ exp_condition, data = _)
```

```{r}
df |> 
  mutate(
    exp_polinfo = factor(exp_polinfo,
                         levels = c("No, I do not want to see information on how to get more involved in democracy",
                                    "Yes, I want to see information on how to get more involved in democracy"),
                         labels = c("No", "Yes"))) |> 
  select(exp_polinfo, exp_polinfo_time) |> 
  datasummary_skim()  
```

```{r}
df |> 
  filter(exp_polinfo == "Yes, I want to see information on how to get more involved in democracy") |> 
  datasummary(exp_polinfo_time ~ exp_condition * (Mean + Median + SD),
              data = _,
              fmt = 2)  
```

```{r}
df |> 
  filter(exp_polinfo == "Yes, I want to see information on how to get more involved in democracy") |> 
  filter(exp_polinfo_time < 150) |>
  ggplot(aes(x = exp_condition, y = exp_polinfo_time,
             fill = exp_condition, color = exp_condition)) +
  geom_rain(
    alpha = 0.5,
    boxplot.args = list(color = "black", outlier.shape = NA)
  ) +
  stat_summary(
    fun = mean,
    geom = "point",
    size = 4,
    fill = "white",
    shape = 21,
    stroke = 1
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  labs(
    title = "Time Spent on Political Information",
    x = "Experimental Condition",
    y = "Time (seconds)" # Add a y-axis label
  ) +
  theme(
    legend.position = "none"
  )
```

## Main Models to Estimate the ATEs

```{r}
# Model data
df_info <- df |> 
  mutate(
    polinfo_choice = case_when(
      exp_polinfo == "No, I do not want to see information on how to get more involved in democracy" ~ 0,
      exp_polinfo == "Yes, I want to see information on how to get more involved in democracy" ~ 1,
      TRUE ~ NA_integer_),
    polinfo_time = exp_polinfo_time
  ) |> 
  mutate(
    polinfo = if_else(polinfo_choice == 1, polinfo_time, 0)
  )
```

```{r}
# brms settings
bayes_seed <- 42
chains <- 4
iter <- 4000
warmup <- floor(iter/2)
adapt_delta <- 0.90
max_treedepth <- 10
```

```{r}
# marginaleffects settings
options(marginaleffects_posterior_interval = "hdi")
options(marginaleffects_posterior_center = stats::median)
```

### Model 1 

```{r}
f_hu1 <- bf(
  polinfo ~ exp_condition,
  hu ~ exp_condition)

priors_hu1 <- c(
  prior(normal(2, 1.5), class = "Intercept"),
  prior(normal(0, 1), class = "b"),
  prior(normal(0, 1), class = "Intercept", dpar = "hu"),
  prior(normal(0, 1), class = "b", dpar = "hu"),
  prior(exponential(1), class = "sigma")
)
```

```{r}
#| output: false
hu1 <- brm(
  data = df_info,
  formula = f_hu1,
  family = hurdle_lognormal(),
  prior = priors_hu1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth
  ),
  file = here(model_dir, "hu1.rds")
)
```

```{r}
print(hu1)
```

#### Quantities of interest

##### Initiation of Information Seeking

```{r}
iis1_pred_avg <- avg_predictions(hu1,
                               dpar = "hu",) |> 
  as_tibble() |> 
  mutate(Median = 1 - estimate,
         "95% HDI Lower" = 1 - conf.high,
         "95% HDI Upper" = 1 - conf.low
         ) |> 
  select(Median,
         "95% HDI Lower",
         "95% HDI Upper" 
         ) 

iis1_pred_avg |> tt()
```

```{r}
iis1_pred <- avg_predictions(hu1, 
                             dpar = "hu",
                             by = "exp_condition") |> 
  as_tibble() |> 
  # Flip the direction as hu models decision NOT to view
  mutate(Median = 1 - estimate,
         "95% HDI Lower" = 1 - conf.high,
         "95% HDI Upper" = 1 - conf.low
         ) |> 
  select(Condition = exp_condition,
         Median,
         "95% HDI Lower",
         "95% HDI Upper" 
         ) 

iis1_pred |> tt()
```

```{r}
iis1_comp <- avg_comparisons(hu1, 
                            dpar = "hu", 
                            variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

iis1_comp |> tt()
```

##### Extent of Information Seeking

```{r}
eis1_pred_avg <- avg_predictions(hu1,
                                dpar = "mu",
                                transform = exp # Translates the log-scale mu to the natural scale median
                                ) |> 
  as_tibble() |> 
  select(Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high 
         ) 

eis1_pred_avg |> tt()
```

```{r}
eis1_pred <- avg_predictions(hu1, 
                             dpar = "mu",
                             by = "exp_condition",
                             transform = exp) |> 
  as_tibble() |> 
  select(Condition = exp_condition,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high 
         ) 

eis1_pred |> tt()
```

```{r}
eis1_comp <- avg_comparisons(hu1, 
                             dpar = "mu",
                             comparison = function(hi, lo) exp(hi) - exp(lo),
                             variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

eis1_comp |> tt()
```

### Model 2 — Interaction with Age Group

```{r}
f_hu2 <- bf(
  polinfo ~ exp_condition * age_group,
  hu ~ exp_condition * age_group)
```

```{r}
#| output: false
hu2 <- brm(
  data = df_info,
  formula = f_hu2,
  family = hurdle_lognormal(),
  prior = priors_hu1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth
  ),
  file = here(model_dir, "hu2.rds")
)
```

```{r}
summary(hu2)
```

#### Quantities of interest

##### Initiation of Information Seeking

```{r}
iis2_comp <- avg_comparisons(hu2, 
                             dpar = "hu", 
                             variables = list(exp_condition = "pairwise"), 
                             by = "age_group") |> 
  as_tibble() |> 
  select(Contrast = contrast,
         `Age Group` = age_group,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 4)))

iis2_comp |> tt()
```

##### Extent of Information Seeking

```{r}
eis2_comp <- avg_comparisons(hu2, 
                             dpar = "mu",
                             variables = list(exp_condition = "pairwise"), 
                             comparison = function(hi, lo) exp(hi) - exp(lo),
                             by = "age_group") |> 
  as_tibble() |> 
  select(Contrast = contrast,
         `Age Group` = age_group,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
         ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 4)))

eis2_comp |> tt()
```

### Model 3 — Interaction with Gender

```{r}
f_hu3 <- bf(
  polinfo ~ exp_condition * gender,
  hu ~ exp_condition * gender)
```

```{r}
#| output: false
hu3 <- brm(
  data = df_info,
  formula = f_hu3,
  family = hurdle_lognormal(),
  prior = priors_hu1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth
  ),
  file = here(model_dir, "hu3.rds")
)
```

```{r}
summary(hu3)
```

#### Quantities of interest

##### Initiation of Information Seeking

```{r}
iis5_comp <- avg_comparisons(hu3, 
                            dpar = "hu", 
                            variables = list(exp_condition = "pairwise"), 
                            by = "gender") |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Gender = gender,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 4)))

iis5_comp |> tt()
```

##### Extent of Information Seeking

```{r}
eis5_comp <- avg_comparisons(hu3, 
                             dpar = "mu",
                             variables = list(exp_condition = "pairwise"), 
                             comparison = function(hi, lo) exp(hi) - exp(lo),
                             by = "gender") |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Gender = gender,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 4)))

eis5_comp |> tt()
```

## Supplementary Models

### Model 4 — Control for Demographics

```{r}
df_control <- df_info |> 
  mutate(ideology = left_right / 10,
         education_level = coalesce(education_level, education)) |> 
  droplevels()

f_hu4 <- bf(
  polinfo ~ exp_condition + scale(age) + gender + ideology + education_level + living_standard,
  hu ~ exp_condition + scale(age) + gender + ideology + education_level + living_standard)
```

```{r}
#| output: false
hu4 <- brm(
  data = df_control,
  formula = f_hu4,
  family = hurdle_lognormal(),
  prior = priors_hu1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth
  ),
  file = here(model_dir, "hu4.rds")
)
```

```{r}
print(hu4)
```

#### Quantities of interest

##### Initiation of Information Seeking

```{r}
iis4_comp <- avg_comparisons(hu4, 
                             dpar = "hu", 
                             variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

iis4_comp |> tt()
```

##### Extent of Information Seeking

```{r}
eis4_comp <- avg_comparisons(hu4, 
                             dpar = "mu",
                             comparison = function(hi, lo) exp(hi) - exp(lo),
                             variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

eis4_comp |> tt()
```

### Model 5 — Pre-Registered Sample Only

Participants aged 16-21 or participants who were recontacted:
```{r}
df_info_prereg <- df_info |> 
  filter(age_group == "16-21 years" | sample_type == "recontact")
```

```{r}
#| output: false
hu5 <- brm(
  data = df_info_prereg,
  formula = f_hu1,
  family = hurdle_lognormal(),
  prior = priors_hu1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth
  ),
  file = here(model_dir, "hu5.rds")
)
```

```{r}
print(hu5)
```

#### Quantities of interest

##### Initiation of Information Seeking

```{r}
iis3_comp <- avg_comparisons(hu5, 
                            dpar = "hu", 
                            variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

iis3_comp |> tt()
```

##### Extent of Informatoin Seeking

```{r}
eis3_comp <- avg_comparisons(hu5, 
                             dpar = "mu",
                             comparison = function(hi, lo) exp(hi) - exp(lo),
                             variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

eis3_comp |> tt()
```

### Model 6 — Attentive Participants Only 

Attentive participants:
```{r}
df_info_att <- df_info |> 
  filter(exp_attention == "Costs of living",
         pre_attention1 == "passed",
         pre_attention2 == "passed",
         pre_attention3 == "passed",
         post_attention1 == "passed")
```

```{r}
#| output: false
hu6 <- brm(
  data = df_info_att,
  formula = f_hu1,
  family = hurdle_lognormal(),
  prior = priors_hu1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth
  ),
  file = here(model_dir, "hu6.rds")
)
```

```{r}
print(hu6)
```

#### Quantities of interest

##### Initiation of Information Seeking

```{r}
iis6_comp <- avg_comparisons(hu6, 
                             dpar = "hu", 
                             variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

iis6_comp |> tt()
```

##### Extent of Information Seeking

```{r}
eis6_comp <- avg_comparisons(hu6, 
                             dpar = "mu",
                             comparison = function(hi, lo) exp(hi) - exp(lo),
                             variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

eis6_comp |> tt()
```

### Model 7 — Check & Handle Outliers

Remove outliers (±3.29 MAD)

```{r}
# Identify outliers using robust z-scores
outliers_mad <- check_outliers(df_info$polinfo_time, 
                               method = "zscore_robust",
                               threshold = 3.29)

outlier_indices <- which(outliers_mad)
```

```{r}
df_info_outlier <- df_info |> 
  slice(-outlier_indices)
```

```{r}
#| output: false
hu7 <- brm(
  data = df_info_outlier,
  formula = f_hu1,
  family = hurdle_lognormal(),
  prior = priors_hu1,
  sample_prior = "yes",
  init = "random",
  chains = chains,
  iter = iter,
  warmup = warmup,
  seed = bayes_seed,
  control = list(
    adapt_delta = adapt_delta,
    max_treedepth = max_treedepth
  ),
  file = here(model_dir, "hu7.rds")
)
```

```{r}
print(hu7)
```

#### Quantities of interest

##### Initiation of Information Seeking

```{r}
iis6_comp <- avg_comparisons(hu7, 
                             dpar = "hu", 
                             variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

iis6_comp |> tt()
```

##### Extent of Information Seeking

```{r}
eis6_comp <- avg_comparisons(hu7, 
                             dpar = "mu",
                             comparison = function(hi, lo) exp(hi) - exp(lo),
                             variables = list(exp_condition = "pairwise")) |> 
  as_tibble() |> 
  select(Contrast = contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high
  ) |> 
  mutate(across(where(is.numeric), \(x) round(x, 3)))

eis6_comp |> tt()
```












