---
title: "Figures and Tables"
description: "Figures and Tables from All Relevant Models" 

format:
  html:
    theme: paper
    shift-heading-level-by: 1
    code-tools: true
    code-fold: true
    toc: true
    toc-fold: false
    toc-location: right
    toc-depth: 4
    toc-title: "Contents"

# Portability settings
embed-resources: true

# Execution options 
execute:
  warning: false
---

```{r}
#| include: false
# set error messages to English
Sys.setenv(LANG = "en")

knitr::opts_chunk$set(
  fig.align = "center", 
  fig.retina = 3,
  fig.width = 6, 
  fig.height = (6 * 0.618),
  out.width = "90%", 
  collapse = FALSE
)

options(
  digits = 4,
  width = 300,
  dplyr.summarise.inform = FALSE)
```

```{r}
#| include: false
#| warning: true
#| message: true
if (!require("groundhog", quietly = TRUE)) {
  install.packages("groundhog")
}
library("groundhog")

# use groundhog to install and load packages
pkgs <- c("here",         # System path management
          "tidyverse",    # ggplot, dplyr, and friends
          "brms",         # Bayesian regression modelling in Stan
          "marginaleffects", # Model-based predictions, comparisons, and more marginalia
          "broom.mixed",  # Tidy model outputs
          "tidybayes",    # Tools to work with Bayesian models 
          "tinytable",    # Minimalist tables
          "modelsummary", # Data and model summaries with tables and plots
          "ggdist",       # Additional plot elements
          "ggrain",       # For fancy raincloud plots
          "GGally",       # ggpairs and other ggplot2 friends
          "ggsignif",     # Add significance to figures
          "ggh4x",        # Additional ggplot2 tools
          "patchwork",    # Combine multiple ggplots
          "showtext"      # Additional fonts for plots etc
          )

groundhog.library(pkgs, "2026-01-01")
```

```{r}
#| include: false

showtext_auto()
showtext_opts(dpi = 600)

font_add_google("Public Sans", "Public Sans")
font_add_google("Public Sans", "Public Sans Light", regular.wt = 300)
font_add_google("Public Sans", "Public Sans Semibold", regular.wt = 600)

# Custom ggplot theme
theme_nice <- function() {
  # General text family and base size
  theme_minimal(base_family = "Public Sans", base_size = 14) +
    theme(
      # Remove minor grid lines for cleaner look
      panel.grid.minor = element_blank(),
      # Customize major grid lines color
      panel.grid.major = element_blank(),
      # Plot title: bold and custom relative size
      plot.title = element_text(family = "Public Sans", face = "bold", size = rel(1.1), margin = margin(b = 10)),
      # Subtitle and caption: lighter weight 
      plot.subtitle = element_text(family = "Public Sans Light", face = "plain"),
      plot.caption = element_text(family = "Public Sans Light", face = "plain"),
      # Axis text: Relative size
      axis.text = element_text(size = rel(0.9)),
      # Axis titles: Semibold and custom relative size
      axis.title = element_text(family = "Public Sans Semibold", size = rel(0.9)),
      axis.title.x = element_text(hjust = 0.5),
      axis.title.y = element_text(hjust = 0.5),
      # Axis lines
      axis.line = element_line(color = "grey25", linewidth = 0.8),
      # Facet labels: bold text on grey background
      strip.text = element_text(
        family = "Public Sans Semibold", face = "plain",
        size = rel(1),
        hjust = 0.5
      ),
      strip.background = element_rect(fill = "grey95", color = "grey25", linewidth = 0.8), 
      # Legend styling: compact and top-positioned
      legend.title = element_text(family = "Public Sans Semibold", size = rel(0.8)),
      legend.text = element_text(size = rel(0.8)),
      legend.position = "top",
      legend.justification = "center",
      legend.title.position = "left",
      legend.margin = margin(l = 0, t = 0)
    )
}


theme_set(theme_nice())
update_geom_defaults("text", list(family = "Public Sans"))
update_geom_defaults("label", list(family = "Public Sans"))
```

```{r}
#| include: false
data_dir <- here("01_data")
table_dir <- here("02_output", "tables")
figure_dir <- here("02_output", "figures")
model_dir <- here("02_output", "models")

dir.create(table_dir, recursive = TRUE, showWarnings = TRUE)
dir.create(figure_dir, recursive = TRUE, showWarnings = TRUE)
dir.create(model_dir, recursive = TRUE, showWarnings = TRUE)
```

```{r}
load(here(data_dir, "analysis", "df_wide.RData"))
df <- df_wide 
rm(df_wide)
```

```{r}
# marginaleffects settings
options(marginaleffects_posterior_interval = "hdi")
options(marginaleffects_posterior_center = stats::median)
```

```{r}
probability_direction <- function(obj, id = "contrast", by = NULL) {
  # Extract posterior draws from marginaleffects object and compute pd per contrast
  # pd = proportion of draws consistent with the direction of the point estimate
  posterior_draws(obj) |>
    group_by(across(all_of(c(id, by)))) |>
    summarise(
      # mean(draw > 0) gives P(effect > 0); pd takes the larger of P(>0) and P(<0)
      pd = (\(p) max(p, 1 - p))(mean(draw > 0)),
      .groups = "drop"
    )
}
```

## RQ 1.1

### Load Models

```{r}
rq1.1.1 <- readRDS(here(model_dir, "RQ1", "m1.rds"))
rq1.1.2 <- readRDS(here(model_dir, "RQ1", "m2.rds"))
rq1.1.3 <- readRDS(here(model_dir, "RQ1", "m3.rds"))
rq1.1.5 <- readRDS(here(model_dir, "RQ1", "m5.rds"))
rq1.1.7 <- readRDS(here(model_dir, "RQ1", "m7.rds"))
```

### Tables

#### RQ1.1 Model Summary Table

```{r}
rq1.1.1_brms <- tidy(rq1.1.1, robust = TRUE, conf.method	= "HPDinterval", rhat = TRUE, ess = TRUE) |> 
  mutate(Model = "Overall")
rq1.1.2_brms <- tidy(rq1.1.2, robust = TRUE, conf.method	= "HPDinterval", rhat = TRUE, ess = TRUE) |> 
  mutate(Model = "Age Group")
rq1.1.3_brms <- tidy(rq1.1.3, robust = TRUE, conf.method	= "HPDinterval", rhat = TRUE, ess = TRUE) |> 
  mutate(Model = "Gender")

rq1.1_brms <- bind_rows(rq1.1.1_brms, rq1.1.2_brms, rq1.1.3_brms) |> 
  filter(effect == "fixed") |> 
  mutate(term = case_when(
    term == "(Intercept)" ~ "Intercept",
    term == "exp_conditionhope" ~ "Hope (vs. Control)",
    term == "exp_conditionanxiety" ~ "Anxiety (vs. Control)",
    term == "age_group22M26years" ~ "Age Group 22-26 (vs. 16-21)",
    term == "exp_conditionhope:age_group22M26years" ~ "Age Group x Hope",
    term == "exp_conditionanxiety:age_group22M26years" ~ "Age Group x Anxiety",
    term == "genderfemale" ~ "Women (vs. Men)",
    term == "genderother" ~ "Other (vs. Men)",
    term == "exp_conditionhope:genderfemale" ~ "Women x Hope",    
    term == "exp_conditionanxiety:genderfemale" ~ "Women x Anxiety",   
    term == "exp_conditionhope:genderother" ~ "Other x Hope",    
    term == "exp_conditionanxiety:genderother" ~ "Other x Anxiety",   
    TRUE ~ term  
  )) |> 
  select(Term = term, 
         Median = estimate, 
         MAD = std.error, 
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         "R-hat" = rhat,
         ESS = ess, 
         Model
         )
```

```{r}
rq1.1_brms_table <- rq1.1_brms |> 
  mutate(across(where(is.numeric), ~round(.x, 3))) |> 
  select(-Model) |> 
  tt() |> 
  group_tt(i = list("Main Model" = 1, "Interaction with Age Group" = 4, "Interaction with Gender" = 10)) 

rq1.1_brms_table

rq1.1_brms_table |> 
  save_tt(here(table_dir, "RQ1", "RQ1.1_brms_table.docx"), overwrite = TRUE)
```

#### RQ1.1 Comparisons Table

```{r}
rq1.1.1_comp_raw <- avg_comparisons(rq1.1.1, variables = list(exp_condition = "pairwise"))
rq1.1.2_comp_raw <- avg_comparisons(rq1.1.2, variables = list(exp_condition = "pairwise"), by = "age_group")
rq1.1.3_comp_raw <- avg_comparisons(rq1.1.3, variables = list(exp_condition = "pairwise"), by = "gender")

rq1.1.1_comp <- rq1.1.1_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq1.1.1_comp_raw), by = "contrast") |>
  mutate(Model = "Overall", Group = "Overall")

rq1.1.2_comp <- rq1.1.2_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq1.1.2_comp_raw, by = "age_group"), by = c("contrast", "age_group")) |>
  mutate(Model = "Age Group") |>
  rename(Group = age_group)

rq1.1.3_comp <- rq1.1.3_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq1.1.3_comp_raw, by = "gender"), by = c("contrast", "gender")) |>
  mutate(Model = "Gender") |>
  rename(Group = gender)

rq1.1_comp <- bind_rows(rq1.1.1_comp, rq1.1.2_comp, rq1.1.3_comp) |>
  mutate(
    Contrast = case_when(
      contrast == "anxiety - control" ~ "Anxiety - Control",
      contrast == "anxiety - hope"    ~ "Anxiety - Hope",
      contrast == "hope - control"    ~ "Hope - Control"),
    Group = case_when(
      Group == "male"   ~ "Men",
      Group == "female" ~ "Women",
      Group == "other"  ~ "Other",
      TRUE ~ Group
    )) |>
  select(Model, Group, Contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         "Probability of Direction" = pd)
```

```{r}
rq1.1_comp_table <- rq1.1_comp |> 
  mutate(across(where(is.numeric), ~round(.x, 3))) |> 
  select(-Model) |> 
  tt() |> 
  group_tt(i = list("Main Model" = 1, "By Age Group" = 4, "By Gender" = 10)) 

rq1.1_comp_table

rq1.1_comp_table |> 
  save_tt(here(table_dir, "RQ1", "RQ1.1_comp_table.docx"), overwrite = TRUE)
```

#### RQ1.1 Pre-Registration Sample Table

```{r}
rq1.1.5_brms <- tidy(rq1.1.5, robust = TRUE, conf.method	= "HPDinterval", rhat = TRUE, ess = TRUE) |> 
  mutate(Model = "Overall") |> 
  filter(effect == "fixed") |> 
  mutate(term = case_when(
    term == "(Intercept)" ~ "Intercept",
    term == "exp_conditionhope" ~ "Hope (vs. Control)",
    term == "exp_conditionanxiety" ~ "Anxiety (vs. Control)",
    TRUE ~ term  
  )) |> 
  select(Term = term, 
         Median = estimate, 
         MAD = std.error, 
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         "R-hat" = rhat,
         ESS = ess, 
         Model
  )
```

```{r}
rq1.1.5_brms_table <- rq1.1.5_brms |> 
  mutate(across(where(is.numeric), ~round(.x, 3))) |> 
  select(-Model) |> 
  tt() 

rq1.1.5_brms_table

rq1.1.5_brms_table |> 
  save_tt(here(table_dir, "RQ1", "prereg_RQ1.1.5_brms_table.docx"), overwrite = TRUE)
```

### Figures 

#### Figure Data

```{r}
# Overall ATE
rq1.1.1.draws <- expand.grid(
  exp_condition = c("control", "anxiety", "hope")
) |>
  add_epred_draws(rq1.1.1, re_formula = NA, ndraws = 4000) |>
  ungroup()

rq1.1.1.contrasts <- rq1.1.1.draws |>
  select(exp_condition, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Anxiety - Hope` = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(
    model = "ATE",
    subgroup = "ATE"
  )

# cATE by age_group
rq1.1.2.draws <- expand.grid(
  exp_condition = c("control", "anxiety", "hope"),
  age_group = unique(df$age_group)
  ) |>
  add_epred_draws(rq1.1.2, re_formula = NA, ndraws = 4000) |>
  ungroup()

rq1.1.2.contrasts <- rq1.1.2.draws |>
  select(exp_condition, age_group, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Anxiety - Hope` = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(
    model = "Age",
    subgroup = as.character(age_group)
  ) |>
  select(-age_group)

# cATE by gender
rq1.1.3.draws <- expand.grid(
  exp_condition = c("control", "anxiety", "hope"),
  gender = unique(df$gender)
) |>
  add_epred_draws(rq1.1.3, re_formula = NA, ndraws = 4000) |>
  ungroup() |> 
  filter(gender != "other")

rq1.1.3.contrasts <- rq1.1.3.draws |>
  select(exp_condition, gender, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Anxiety - Hope` = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(
    model = "Gender",
    subgroup = as.character(gender)
  ) |>
  select(-gender)

rq1.1_posterior_data <- bind_rows(rq1.1.1.contrasts, rq1.1.2.contrasts, rq1.1.3.contrasts) |>
  mutate(
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety − Control", "Hope − Control")),
    model = factor(model, levels = c("ATE", "Age", "Gender"))
  )

# Compute whether HDI excludes zero for each group
rq1.1_hdi_check <- rq1.1_posterior_data |>
  mutate(
    estimate = estimate,
    subgroup = case_when(
      subgroup == "male" ~ "Men",
      subgroup == "female" ~ "Women",
      subgroup == "16-21 years" ~ "16-21",
      subgroup == "22-26 years" ~ "22-26",
      TRUE ~ subgroup
    ),
    subgroup = factor(subgroup, levels = c("ATE", "22-26", "16-21", "Women", "Men"))
  ) |>
  group_by(model, contrast, subgroup) |>
  median_hdi(estimate, .width = 0.95) |>
  mutate(excludes_zero = if_else(sign(.lower) == sign(.upper), "Excludes zero", "Includes zero")) |>
  select(model, contrast, subgroup, excludes_zero)
```

#### RQ1.1 Figure

```{r}
#| fig-height: 5.5
#| fig-width: 8
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)

rq1.1_posterior_data |>
  mutate(
    estimate = estimate * 100,
    subgroup = case_when(
      subgroup == "male" ~ "Men",
      subgroup == "female" ~ "Women",
      subgroup == "16-21 years" ~ "16-21",
      subgroup == "22-26 years" ~ "22-26",
      TRUE ~ subgroup
    ),
    subgroup = factor(subgroup, levels = c("ATE", "22-26", "16-21", "Women", "Men"))
  ) |>
  left_join(rq1.1_hdi_check, by = c("model", "contrast", "subgroup")) |>
  ggplot(aes(x = estimate, y = subgroup, fill = excludes_zero)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  stat_slabinterval(
    .width = c(.95),
    point_interval = "median_hdi",
    scale = 0.7,
    slab_alpha = 0.6,        
    interval_alpha = 1,      
    point_alpha = 1,          
    normalize = "groups",
    point_size = 2.5,
    interval_size = 1.5) +
  facet_grid(model ~ contrast, scales = "free_y", space = "free_y") +
  scale_fill_manual(
    values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
    name = "95% HDI",
  ) +
  # scale_color_manual(
  #   values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
  #   name = "95% HDI",
  # ) +
  scale_x_continuous(limits = c(-10, 10), breaks = seq(-10, 10, by = 5), expand = expansion(add = 2.5)) +
  labs(
    x = "Percentage Points",
    y = NULL,
    title = "Effects on Democratic Support",
    subtitle = "Posterior Distributions with Median and 95% HDI"
  ) +
  theme_nice() +
  theme(
    legend.position = "bottom",
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2)
  ) 

ggsave(here(figure_dir, "RQ1", "RQ1.1_figure.png"),
       height = 5.5,
       width = 8,
       dpi = 600)
```

#### RQ1.1 Item-Level Differences Figure

```{r}
df_dem_items <- df |> 
  select(id, exp_condition, 
         exp_dem_censor_media_rev,
         exp_dem_one_party_rev,
         exp_dem_question_vote_rev,
         exp_dem_respect_elections,
         exp_dem_ignore_courts_rev,
         exp_dem_ignore_parliament_rev,
         exp_dem_bend_law_rev) |> 
  pivot_longer(
    cols = exp_dem_censor_media_rev:exp_dem_bend_law_rev,
    names_to = "item",
    values_to = "response"
  ) |> 
  mutate(
    response_pomp = (response - 1) / (5 - 1),  # Convert 1-5 to 0-1
    item = factor(item, 
                  levels = c("exp_dem_censor_media_rev",
                            "exp_dem_one_party_rev",
                            "exp_dem_question_vote_rev",
                            "exp_dem_respect_elections",
                            "exp_dem_ignore_courts_rev",
                            "exp_dem_ignore_parliament_rev",
                            "exp_dem_bend_law_rev"),
                  labels = c("FreeExp", "FreeAssc", "UniSuff", 
                            "FFElect", "JudCnstr", "LegCnstr", "EqLaw"))
  )

# Get posterior predictions 
rq1.1.7.draws <- expand.grid(
  exp_condition = c("control", "anxiety", "hope"),
  item = levels(df_dem_items$item)) |>
  add_epred_draws(rq1.1.7, re_formula = NA, ndraws = 4000) |>
  ungroup()

# Compute item-level pairwise contrasts 
rq1.1.7.item_contrasts <- rq1.1.7.draws |>
  select(exp_condition, item, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Anxiety - Hope` = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(type = "Item-level")

# Compute pairwise comparisons across items
rq1.1.7.avg_contrasts <- rq1.1.7.item_contrasts |>
  group_by(contrast, .draw) |>
  summarise(estimate = mean(estimate), .groups = "drop") |>
  mutate(
    item = "Overall ATE",
    type = "Overall"
  )

# Combine draws
rq1.1.7.contrasts <- bind_rows(rq1.1.7.item_contrasts, rq1.1.7.avg_contrasts) |>
  mutate(
    item = factor(item, levels = c(levels(df_dem_items$item), "Overall ATE")),
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety − Control", "Hope − Control"))
  )

# Compute whether HDI excludes zero for each item
rq1.1.7.hdi_check <- rq1.1.7.contrasts |>
  mutate(estimate = estimate * 100) |>
  group_by(item, contrast) |>
  median_hdi(estimate, .width = 0.95) |>
  mutate(excludes_zero = if_else(sign(.lower) == sign(.upper), "Excludes zero", "Includes zero")) |>
  select(item, contrast, excludes_zero)
```

```{r}
#| fig-height: 5
#| fig-width: 10
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)

rq1.1.7.contrasts |>
  mutate(estimate = estimate * 100) |>
  left_join(rq1.1.7.hdi_check, by = c("item", "contrast")) |>
  ggplot(aes(x = estimate, y = item, fill = excludes_zero)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  stat_slabinterval(
    .width = c(.95),
    point_interval = "median_hdi",
    scale = 0.7,
    slab_alpha = 0.6,        
    interval_alpha = 1,      
    point_alpha = 1,          
    normalize = "groups",
    point_size = 2.5,
    interval_size = 1.5) +
  facet_wrap(~contrast) +
  scale_fill_manual(
    name = "95% HDI",
    values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
  ) +
  # scale_color_manual(
  #   name = "95% HDI",
  #   values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
  # ) +
  scale_x_continuous(limits = c(-15, 15), breaks = seq(-10, 10, by = 5), expand = expansion(add = 2.5)) +
  labs(
    x = "Percentage Points",
    y = NULL,
    title = "Treatment Effects on Democratic Support",
    subtitle = "Posterior Distributions with Median and 95% HDI"
  ) +
  theme_nice() +
  theme(
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2),
    legend.position = "bottom"
  )

ggsave(here(figure_dir, "RQ1", "RQ1.1_item_figure.png"),
       height = 5,
       width = 10,
       dpi = 600)
```

## RQ 1.2

```{r}
rq1.2.1 <- readRDS(here(model_dir, "RQ1", "cj1.rds"))
rq1.2.2 <- readRDS(here(model_dir, "RQ1", "cj2.rds"))
rq1.2.3 <- readRDS(here(model_dir, "RQ1", "cj3.rds"))
rq1.2.5 <- readRDS(here(model_dir, "RQ1", "cj5.rds"))
```

### Tables

#### RQ1.2 Model Summary Table

```{r}
conjoint_controls <- c(
  "b_conjoint_sexFemale", "b_conjoint_age_z",
  "b_conjoint_partyConservatives", "b_conjoint_partyLiberalDemocrats",
  "b_conjoint_partyGreenParty", "b_conjoint_partyReformUK",
  "b_conjoint_ecoEconomicallygood", "b_conjoint_ecoEconomicallybad",
  "prior_b"
)

rq1.2.1_brms <- bind_rows(
  tidy(rq1.2.1, parameters = "b",    robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE),
  tidy(rq1.2.1, parameters = "^sd_", robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE)
) |> mutate(Model = "Overall")

rq1.2.2_brms <- bind_rows(
  tidy(rq1.2.2, parameters = "b",    robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE),
  tidy(rq1.2.2, parameters = "^sd_", robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE)
) |> mutate(Model = "Age Group")

rq1.2.3_brms <- bind_rows(
  tidy(rq1.2.3, parameters = "b",    robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE),
  tidy(rq1.2.3, parameters = "^sd_", robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE)
) |> mutate(Model = "Gender")

rq1.2_brms <- bind_rows(rq1.2.1_brms, rq1.2.2_brms, rq1.2.3_brms) |>
  filter(!term %in% conjoint_controls) |>
  mutate(term = str_remove(term, "^b_")) |>
  mutate(term = case_when(
    term == "(Intercept)"                                                      ~ "Intercept",
    term == "conjoint_demDemocratic"                                           ~ "Democratic (vs. Undemocratic)",
    term == "exp_conditionhope"                                                ~ "Hope (vs. Control)",
    term == "exp_conditionanxiety"                                             ~ "Anxiety (vs. Control)",
    term == "conjoint_demDemocratic:exp_conditionhope"                         ~ "Democratic × Hope",
    term == "conjoint_demDemocratic:exp_conditionanxiety"                      ~ "Democratic × Anxiety",
    term == "sd_id__(Intercept)"                                               ~ "SD(Intercept)",
    term == "age_group22M26years"                                              ~ "Age Group 22-26 (vs. 16-21)",
    term == "conjoint_demDemocratic:age_group22M26years"                       ~ "Democratic × Age Group",
    term == "exp_conditionhope:age_group22M26years"                            ~ "Age Group × Hope",
    term == "exp_conditionanxiety:age_group22M26years"                         ~ "Age Group × Anxiety",
    term == "conjoint_demDemocratic:exp_conditionhope:age_group22M26years"     ~ "Democratic × Hope × Age Group",
    term == "conjoint_demDemocratic:exp_conditionanxiety:age_group22M26years"  ~ "Democratic × Anxiety × Age Group",
    term == "genderfemale"                                                     ~ "Women (vs. Men)",
    term == "genderother"                                                      ~ "Other (vs. Men)",
    term == "conjoint_demDemocratic:genderfemale"                              ~ "Democratic × Women",
    term == "conjoint_demDemocratic:genderother"                               ~ "Democratic × Other",
    term == "exp_conditionhope:genderfemale"                                   ~ "Women × Hope",
    term == "exp_conditionanxiety:genderfemale"                                ~ "Women × Anxiety",
    term == "exp_conditionhope:genderother"                                    ~ "Other × Hope",
    term == "exp_conditionanxiety:genderother"                                 ~ "Other × Anxiety",
    term == "conjoint_demDemocratic:exp_conditionhope:genderfemale"            ~ "Democratic × Hope × Women",
    term == "conjoint_demDemocratic:exp_conditionanxiety:genderfemale"         ~ "Democratic × Anxiety × Women",
    term == "conjoint_demDemocratic:exp_conditionhope:genderother"             ~ "Democratic × Hope × Other",
    term == "conjoint_demDemocratic:exp_conditionanxiety:genderother"          ~ "Democratic × Anxiety × Other",
    TRUE ~ term
  )) |>
  select(Term = term, Median = estimate, MAD = std.error,
         "95% HDI Lower" = conf.low, "95% HDI Upper" = conf.high,
         "R-hat" = rhat, ESS = ess, Model)

n1 <- rq1.2_brms |> filter(Model == "Overall") |> nrow()
n2 <- rq1.2_brms |> filter(Model == "Age Group") |> nrow()
```

```{r}
rq1.2_brms_table <- rq1.2_brms |>
  mutate(across(where(is.numeric), ~round(.x, 3))) |>
  select(-Model) |>
  tt(notes = "Note. All models control for conjoint attributes: candidate sex, age, political party, and economic reputation.") |>
  group_tt(i = list(
    "Main Model" = 1,
    "Interaction with Age Group" = n1 + 1,
    "Interaction with Gender" = n1 + n2 + 1
  ))

rq1.2_brms_table
rq1.2_brms_table |>
  save_tt(here(table_dir, "RQ1", "RQ1.2_brms_table.docx"), overwrite = TRUE)
```

#### RQ1.2 Comparisons Table

```{r}
rq1.2.1_comp_raw <- avg_comparisons(rq1.2.1, variables = list(conjoint_dem = "pairwise"), by = "exp_condition", hypothesis = ~pairwise)
rq1.2.2_comp_raw <- avg_comparisons(rq1.2.2, variables = list(conjoint_dem = "pairwise"), by = c("exp_condition", "age_group"), hypothesis = ~pairwise)
rq1.2.3_comp_raw <- avg_comparisons(rq1.2.3, variables = list(conjoint_dem = "pairwise"), by = c("exp_condition", "gender"), hypothesis = ~pairwise)

within_age <- c(
  "(hope 16-21 years) - (control 16-21 years)",
  "(anxiety 16-21 years) - (control 16-21 years)",
  "(anxiety 16-21 years) - (hope 16-21 years)",
  "(hope 22-26 years) - (control 22-26 years)",
  "(anxiety 22-26 years) - (control 22-26 years)",
  "(anxiety 22-26 years) - (hope 22-26 years)"
)

within_gender <- c(
  "(hope male) - (control male)",
  "(anxiety male) - (control male)",
  "(anxiety male) - (hope male)",
  "(hope female) - (control female)",
  "(anxiety female) - (control female)",
  "(anxiety female) - (hope female)",
  "(hope other) - (control other)",
  "(anxiety other) - (control other)",
  "(anxiety other) - (hope other)"
)

rq1.2.1_comp <- rq1.2.1_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq1.2.1_comp_raw, id = "hypothesis"), by = "hypothesis") |>
  mutate(Model = "Overall", Group = "Overall")

rq1.2.2_comp <- rq1.2.2_comp_raw |>
  as_tibble() |>
  filter(hypothesis %in% within_age) |>
  left_join(
    posterior_draws(rq1.2.2_comp_raw) |>
      filter(hypothesis %in% within_age) |>
      group_by(hypothesis) |>
      summarise(pd = (\(p) max(p, 1 - p))(mean(draw > 0)), .groups = "drop"),
    by = "hypothesis"
  ) |>
  mutate(
    Model = "Age Group",
    Group = case_when(
      str_detect(hypothesis, "16-21") ~ "16-21 years",
      str_detect(hypothesis, "22-26") ~ "22-26 years"
    )
  )

rq1.2.3_comp <- rq1.2.3_comp_raw |>
  as_tibble() |>
  filter(hypothesis %in% within_gender) |>
  left_join(
    posterior_draws(rq1.2.3_comp_raw) |>
      filter(hypothesis %in% within_gender) |>
      group_by(hypothesis) |>
      summarise(pd = (\(p) max(p, 1 - p))(mean(draw > 0)), .groups = "drop"),
    by = "hypothesis"
  ) |>
  mutate(
    Model = "Gender",
    Group = case_when(
      str_detect(hypothesis, "female") ~ "Women",
      str_detect(hypothesis, "male")   ~ "Men",
      str_detect(hypothesis, "other")  ~ "Other")
  )

rq1.2_comp <- bind_rows(rq1.2.1_comp, rq1.2.2_comp, rq1.2.3_comp) |>
  mutate(Contrast = case_when(
    str_detect(hypothesis, "^\\(hope")    & str_detect(hypothesis, "control") ~ "Hope - Control",
    str_detect(hypothesis, "^\\(anxiety") & str_detect(hypothesis, "control") ~ "Anxiety - Control",
    str_detect(hypothesis, "^\\(anxiety") & str_detect(hypothesis, "hope")    ~ "Anxiety - Hope"
  )) |>
  select(Model, Group, Contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         "Probability of Direction" = pd)

n1 <- rq1.2_comp |> filter(Model == "Overall") |> nrow()
n2 <- rq1.2_comp |> filter(Model == "Age Group") |> nrow()
```

```{r}
rq1.2_comp_table <- rq1.2_comp |>
  mutate(across(where(is.numeric), ~round(.x, 3))) |>
  select(-Model) |>
  tt() |>
  group_tt(i = list("Main Model" = 1, "By Age Group" = n1 + 1, "By Gender" = n1 + n2 + 1))

rq1.2_comp_table
rq1.2_comp_table |>
  save_tt(here(table_dir, "RQ1", "RQ1.2_comp_table.docx"), overwrite = TRUE)
```

#### RQ1.2 Pre-Registration Sample Table

```{r}
rq1.2.5_brms <- bind_rows(
  tidy(rq1.2.5, parameters = "b",    robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE),
  tidy(rq1.2.5, parameters = "^sd_", robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE)
) |>
  filter(!term %in% conjoint_controls) |>
  mutate(term = str_remove(term, "^b_")) |>
  mutate(term = case_when(
    term == "(Intercept)"                                ~ "Intercept",
    term == "conjoint_demDemocratic"                    ~ "Democratic (vs. Undemocratic)",
    term == "exp_conditionhope"                         ~ "Hope (vs. Control)",
    term == "exp_conditionanxiety"                      ~ "Anxiety (vs. Control)",
    term == "conjoint_demDemocratic:exp_conditionhope"  ~ "Democratic × Hope",
    term == "conjoint_demDemocratic:exp_conditionanxiety" ~ "Democratic × Anxiety",
    term == "sd_id__(Intercept)"                        ~ "SD(Intercept)",
    TRUE ~ term
  )) |>
  select(Term = term, Median = estimate, MAD = std.error,
         "95% HDI Lower" = conf.low, "95% HDI Upper" = conf.high,
         "R-hat" = rhat, ESS = ess)
```

```{r}
rq1.2.5_brms_table <- rq1.2.5_brms |>
  mutate(across(where(is.numeric), ~round(.x, 3))) |>
  tt(notes = "Note. Model controls for conjoint attributes: candidate sex, age, political party, and economic reputation.")

rq1.2.5_brms_table
rq1.2.5_brms_table |>
  save_tt(here(table_dir, "RQ1", "prereg_RQ1.2.5_brms_table.docx"), overwrite = TRUE)
```

### Figures 

#### Figure Data

```{r}
rq1.2.1.cAMCEs <- avg_slopes(rq1.2.1, variables = "conjoint_dem", by = "exp_condition", re_formula = NA) |>
  posterior_draws()

rq1.2.1.contrasts <- rq1.2.1.cAMCEs |>
  select(drawid, exp_condition, draw) |>
  pivot_wider(names_from = exp_condition, values_from = draw) |>
  mutate(
    `Anxiety - Control` = anxiety - control,
    `Hope - Control`    = hope - control,
    `Anxiety - Hope`    = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety - Control`, `Hope - Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(model = "ATE", subgroup = "ATE")

rq1.2.2.cAMCEs <- avg_slopes(rq1.2.2, variables = "conjoint_dem", by = c("exp_condition", "age_group"), re_formula = NA) |>
  posterior_draws()

rq1.2.2.contrasts <- rq1.2.2.cAMCEs |>
  select(drawid, exp_condition, age_group, draw) |>
  pivot_wider(names_from = exp_condition, values_from = draw) |>
  mutate(
    `Anxiety - Control` = anxiety - control,
    `Hope - Control`    = hope - control,
    `Anxiety - Hope`    = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety - Control`, `Hope - Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(model = "Age", subgroup = as.character(age_group)) |>
  select(-age_group)

rq1.2.3.cAMCEs <- avg_slopes(rq1.2.3, variables = "conjoint_dem", by = c("exp_condition", "gender"), re_formula = NA) |>
  posterior_draws()

rq1.2.3.contrasts <- rq1.2.3.cAMCEs |>
  select(drawid, exp_condition, gender, draw) |>
  pivot_wider(names_from = exp_condition, values_from = draw) |>
  mutate(
    `Anxiety - Control` = anxiety - control,
    `Hope - Control`    = hope - control,
    `Anxiety - Hope`    = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety - Control`, `Hope - Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(model = "Gender", subgroup = as.character(gender)) |>
  select(-gender)

rq1.2_posterior_data <- bind_rows(rq1.2.1.contrasts, rq1.2.2.contrasts, rq1.2.3.contrasts) |>
  filter(subgroup != "other") |>
  mutate(
    subgroup = case_when(
      subgroup == "male"       ~ "Men",
      subgroup == "female"     ~ "Women",
      subgroup == "16-21 years" ~ "16-21",
      subgroup == "22-26 years" ~ "22-26",
      TRUE ~ subgroup
    ),
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety - Control", "Hope - Control")),
    model    = factor(model, levels = c("ATE", "Age", "Gender")),
    subgroup = factor(subgroup, levels = c("ATE", "22-26", "16-21", "Women", "Men"))
  )

rq1.2_hdi_check <- rq1.2_posterior_data |>
  group_by(model, contrast, subgroup) |>
  median_hdi(estimate, .width = 0.95) |>
  mutate(excludes_zero = if_else(sign(.lower) == sign(.upper), "Excludes zero", "Includes zero")) |>
  select(model, contrast, subgroup, excludes_zero)
```

#### RQ1.2 Figure

```{r}
#| fig-height: 5.5
#| fig-width: 8
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)

rq1.2_posterior_data |>
  mutate(estimate = estimate * 100) |>
  left_join(rq1.2_hdi_check, by = c("model", "contrast", "subgroup")) |>
  ggplot(aes(x = estimate, y = subgroup, fill = excludes_zero)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  stat_slabinterval(
    .width = c(.95),
    point_interval = "median_hdi",
    scale = 0.7,
    slab_alpha = 0.6,
    interval_alpha = 1,
    point_alpha = 1,
    normalize = "groups",
    point_size = 2.5,
    interval_size = 1.5
  ) +
  facet_grid(model ~ contrast, scales = "free_y", space = "free_y") +
  scale_fill_manual(
    values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
    name = "95% HDI"
  ) +
  scale_x_continuous(limits = c(-20, 20), breaks = seq(-15, 15, by = 5), expand = expansion(add = 0.5)) +
  labs(
    x = "Percentage Points",
    y = NULL,
    title = "Effects on Democratic Candidate Preference",
    subtitle = "Posterior Distributions with Median and 95% HDI"
  ) +
  theme_nice() +
  theme(
    legend.position = "bottom",
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2)
  )

ggsave(here(figure_dir, "RQ1", "RQ1.2_figure.png"),
       height = 5.5,
       width = 8,
       dpi = 600)
```

## RQ 2.1 

```{r}
rq2.1.1 <- readRDS(here(model_dir, "RQ2", "m1.rds"))
rq2.1.2 <- readRDS(here(model_dir, "RQ2", "m2.rds"))
rq2.1.3 <- readRDS(here(model_dir, "RQ2", "m3.rds"))
rq2.1.5 <- readRDS(here(model_dir, "RQ2", "m5.rds"))
rq2.1.7 <- readRDS(here(model_dir, "RQ2", "m7.rds"))
```

### Tables

#### RQ2.1 Model Summary Table

```{r}
rq2.1.1_brms <- tidy(rq2.1.1, robust = TRUE, conf.method	= "HPDinterval", rhat = TRUE, ess = TRUE) |> 
  mutate(Model = "Overall")
rq2.1.2_brms <- tidy(rq2.1.2, robust = TRUE, conf.method	= "HPDinterval", rhat = TRUE, ess = TRUE) |> 
  mutate(Model = "Age Group")
rq2.1.3_brms <- tidy(rq2.1.3, robust = TRUE, conf.method	= "HPDinterval", rhat = TRUE, ess = TRUE) |> 
  mutate(Model = "Gender")

rq2.1_brms <- bind_rows(rq2.1.1_brms, rq2.1.2_brms, rq2.1.3_brms) |> 
  filter(effect == "fixed") |> 
  mutate(term = case_when(
    term == "(Intercept)" ~ "Intercept",
    term == "exp_conditionhope" ~ "Hope (vs. Control)",
    term == "exp_conditionanxiety" ~ "Anxiety (vs. Control)",
    term == "age_group22M26years" ~ "Age Group 22-26 (vs. 16-21)",
    term == "exp_conditionhope:age_group22M26years" ~ "Age Group x Hope",
    term == "exp_conditionanxiety:age_group22M26years" ~ "Age Group x Anxiety",
    term == "genderfemale" ~ "Women (vs. Men)",
    term == "genderother" ~ "Other (vs. Men)",
    term == "exp_conditionhope:genderfemale" ~ "Women x Hope",    
    term == "exp_conditionanxiety:genderfemale" ~ "Women x Anxiety",   
    term == "exp_conditionhope:genderother" ~ "Other x Hope",    
    term == "exp_conditionanxiety:genderother" ~ "Other x Anxiety",   
    TRUE ~ term  
  )) |> 
  select(Term = term, 
         Median = estimate, 
         MAD = std.error, 
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         "R-hat" = rhat,
         ESS = ess, 
         Model
  )
```

```{r}
rq2.1_brms_table <- rq2.1_brms |> 
  mutate(across(where(is.numeric), ~round(.x, 3))) |> 
  select(-Model) |> 
  tt() |> 
  group_tt(i = list("Main Model" = 1, "Interaction with Age Group" = 4, "Interaction with Gender" = 10)) 

rq2.1_brms_table

rq2.1_brms_table |> 
  save_tt(here(table_dir, "RQ2", "rq2.1_brms_table.docx"), overwrite = TRUE)
```

#### RQ2.1 Comparison Table

```{r}
rq2.1.1_comp_raw <- avg_comparisons(rq2.1.1, variables = list(exp_condition = "pairwise"))
rq2.1.2_comp_raw <- avg_comparisons(rq2.1.2, variables = list(exp_condition = "pairwise"), by = "age_group")
rq2.1.3_comp_raw <- avg_comparisons(rq2.1.3, variables = list(exp_condition = "pairwise"), by = "gender")

rq2.1.1_comp <- rq2.1.1_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq2.1.1_comp_raw), by = "contrast") |>
  mutate(Model = "Overall", Group = "Overall")

rq2.1.2_comp <- rq2.1.2_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq2.1.2_comp_raw, by = "age_group"), by = c("contrast", "age_group")) |>
  mutate(Model = "Age Group") |>
  rename(Group = age_group)

rq2.1.3_comp <- rq2.1.3_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq2.1.3_comp_raw, by = "gender"), by = c("contrast", "gender")) |>
  mutate(Model = "Gender") |>
  rename(Group = gender)

rq2.1_comp <- bind_rows(rq2.1.1_comp, rq2.1.2_comp, rq2.1.3_comp) |>
  mutate(
    Contrast = case_when(
      contrast == "anxiety - control" ~ "Anxiety - Control",
      contrast == "anxiety - hope"    ~ "Anxiety - Hope",
      contrast == "hope - control"    ~ "Hope - Control"),
    Group = case_when(
      Group == "male"   ~ "Men",
      Group == "female" ~ "Women",
      Group == "other"  ~ "Other",
      TRUE ~ Group
    )) |>
  select(Model, Group, Contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         "Probability of Direction" = pd)
```

```{r}
rq2.1_comp_table <- rq2.1_comp |> 
  mutate(across(where(is.numeric), ~round(.x, 3))) |> 
  select(-Model) |> 
  tt() |> 
  group_tt(i = list("Main Model" = 1, "By Age Group" = 4, "By Gender" = 10)) 

rq2.1_comp_table

rq2.1_comp_table |> 
  save_tt(here(table_dir, "RQ2", "rq2.1_comp_table.docx"), overwrite = TRUE)
```

#### RQ2.1 Pre-Registration Sample Table

```{r}
rq2.1.5_brms <- tidy(rq2.1.5, robust = TRUE, conf.method	= "HPDinterval", rhat = TRUE, ess = TRUE) |> 
  mutate(Model = "Overall") |> 
  filter(effect == "fixed") |> 
  mutate(term = case_when(
    term == "(Intercept)" ~ "Intercept",
    term == "exp_conditionhope" ~ "Hope (vs. Control)",
    term == "exp_conditionanxiety" ~ "Anxiety (vs. Control)",
    TRUE ~ term  
  )) |> 
  select(Term = term, 
         Median = estimate, 
         MAD = std.error, 
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         "R-hat" = rhat,
         ESS = ess, 
         Model
  )
```

```{r}
rq2.1.5_brms_table <- rq2.1.5_brms |> 
  mutate(across(where(is.numeric), ~round(.x, 3))) |> 
  select(-Model) |> 
  tt() 

rq2.1.5_brms_table

rq2.1.5_brms_table |> 
  save_tt(here(table_dir, "RQ2", "prereg_rq2.1.5_brms_table.docx"), overwrite = TRUE)
```

### Figures

#### Figure Data

```{r}
# rq2.1.1: Overall ATE
rq2.1.1.draws <- expand.grid(
  exp_condition = c("control", "anxiety", "hope")
) |>
  add_epred_draws(rq2.1.1, re_formula = NA, ndraws = 4000) |>
  ungroup()

rq2.1.1.contrasts <- rq2.1.1.draws |>
  select(exp_condition, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Anxiety - Hope` = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(
    model = "ATE",
    subgroup = "ATE"
  )

# rq2.1.2: cATE by age_group
rq2.1.2.draws <- expand.grid(
  exp_condition = c("control", "anxiety", "hope"),
  age_group = unique(df$age_group)
) |>
  add_epred_draws(rq2.1.2, re_formula = NA, ndraws = 4000) |>
  ungroup()

rq2.1.2.contrasts <- rq2.1.2.draws |>
  select(exp_condition, age_group, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Anxiety - Hope` = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(
    model = "Age",
    subgroup = as.character(age_group)
  ) |>
  select(-age_group)

# rq2.1.3: cATE by gender
rq2.1.3.draws <- expand.grid(
  exp_condition = c("control", "anxiety", "hope"),
  gender = unique(df$gender)
) |>
  add_epred_draws(rq2.1.3, re_formula = NA, ndraws = 4000) |>
  ungroup() |> 
  filter(gender != "other")

rq2.1.3.contrasts <- rq2.1.3.draws |>
  select(exp_condition, gender, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Anxiety - Hope` = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(
    model = "Gender",
    subgroup = as.character(gender)
  ) |>
  select(-gender)

rq2.1_posterior_data <- bind_rows(rq2.1.1.contrasts, rq2.1.2.contrasts, rq2.1.3.contrasts) |>
  mutate(
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety − Control", "Hope − Control")),
    model = factor(model, levels = c("ATE", "Age", "Gender"))
  )

# Compute whether HDI excludes zero for each group
rq2.1_hdi_check <- rq2.1_posterior_data |>
  mutate(
    estimate = estimate * 100,
    subgroup = case_when(
      subgroup == "male" ~ "Men",
      subgroup == "female" ~ "Women",
      subgroup == "16-21 years" ~ "16-21",
      subgroup == "22-26 years" ~ "22-26",
      TRUE ~ subgroup
    ),
    subgroup = factor(subgroup, levels = c("ATE", "22-26", "16-21", "Women", "Men"))
  ) |>
  group_by(model, contrast, subgroup) |>
  median_hdi(estimate, .width = 0.95) |>
  mutate(excludes_zero = if_else(sign(.lower) == sign(.upper), "Excludes zero", "Includes zero")) |>
  select(model, contrast, subgroup, excludes_zero)
```

#### RQ2.1 Figure

```{r}
#| fig-height: 5.5
#| fig-width: 8
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)

rq2.1_posterior_data |>
  mutate(
    estimate = estimate * 100,
    subgroup = case_when(
      subgroup == "male" ~ "Men",
      subgroup == "female" ~ "Women",
      subgroup == "16-21 years" ~ "16-21",
      subgroup == "22-26 years" ~ "22-26",
      TRUE ~ subgroup
    ),
    subgroup = factor(subgroup, levels = c("ATE", "22-26", "16-21", "Women", "Men"))
  ) |>
  left_join(rq2.1_hdi_check, by = c("model", "contrast", "subgroup")) |>
  ggplot(aes(x = estimate, y = subgroup, fill = excludes_zero)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  stat_slabinterval(
    .width = c(.95),
    point_interval = "median_hdi",
    scale = 0.7,
    slab_alpha = 0.6,        
    interval_alpha = 1,      
    point_alpha = 1,          
    normalize = "groups",
    point_size = 2.5,
    interval_size = 1.5) +
  facet_grid(model ~ contrast, scales = "free_y", space = "free_y") +
  scale_fill_manual(
    values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
    name = "95% HDI",
  ) +
  # scale_color_manual(
  #   values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
  #   name = "95% HDI",
  # ) +
  scale_x_continuous(limits = c(-10, 10), breaks = seq(-10, 10, by = 5), expand = expansion(add = 2.5)) +
  labs(
    x = "Percentage Points",
    y = NULL,
    title = "Effects on Political Participation",
    subtitle = "Posterior Distributions with Median and 95% HDI"
  ) +
  theme_nice() +
  theme(
    legend.position = "bottom",
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2)
  ) 

ggsave(here(figure_dir, "RQ2", "RQ2.1_figure.png"),
       height = 5.5,
       width = 8,
       dpi = 600)
```

#### RQ2.1 Item-Level Differences Figure

```{r}
df_polpart_items <- df |> 
  select(id, exp_condition, 
         exp_polpart_explain_vote,
         exp_polpart_share_story,
         exp_polpart_send_video,
         exp_polpart_discuss_online,
         exp_polpart_protest) |> 
  pivot_longer(
    cols = exp_polpart_explain_vote:exp_polpart_protest,
    names_to = "item",
    values_to = "response"
  ) |> 
  mutate(
    response_pomp = (response - 1) / (5 - 1),  # Convert 1-5 to 0-1
    item = factor(item, 
                  levels = c("exp_polpart_explain_vote",
                             "exp_polpart_share_story",
                             "exp_polpart_send_video",
                             "exp_polpart_discuss_online",
                             "exp_polpart_protest"
                            ),
                  labels = c("ExpVote", "ShareStory", "SendVideo", 
                             "DiscOnl", "Protest"))
  )
```

```{r}
# Get posterior predictions 
rq2.1.7.draws <- expand.grid(
  exp_condition = c("control", "anxiety", "hope"),
  item = levels(df_polpart_items$item)) |>
  add_epred_draws(rq2.1.7, re_formula = NA, ndraws = 4000) |>
  ungroup()

# Compute item-level pairwise contrasts 
rq2.1.7.item_contrasts <- rq2.1.7.draws |>
  select(exp_condition, item, .draw, .epred) |>
  pivot_wider(names_from = exp_condition, values_from = .epred) |>
  mutate(
    `Anxiety − Control` = anxiety - control,
    `Hope − Control` = hope - control,
    `Anxiety - Hope` = anxiety - hope
  ) |>
  pivot_longer(
    cols = c(`Anxiety − Control`, `Hope − Control`, `Anxiety - Hope`),
    names_to = "contrast",
    values_to = "estimate"
  ) |>
  mutate(type = "Item-level")

# Compute pairwise comparisons across items
rq2.1.7.avg_contrasts <- rq2.1.7.item_contrasts |>
  group_by(contrast, .draw) |>
  summarise(estimate = mean(estimate), .groups = "drop") |>
  mutate(
    item = "Overall ATE",
    type = "Overall"
  )

# Combine draws
rq2.1.7.contrasts <- bind_rows(rq2.1.7.item_contrasts, rq2.1.7.avg_contrasts) |>
  mutate(
    item = factor(item, levels = c(levels(df_polpart_items$item), "Overall ATE")),
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety − Control", "Hope − Control"))
  )

# Compute whether HDI excludes zero for each item
rq2.1.7.hdi_check <- rq2.1.7.contrasts |>
  mutate(estimate = estimate * 100) |>
  group_by(item, contrast) |>
  median_hdi(estimate, .width = 0.95) |>
  mutate(excludes_zero = if_else(sign(.lower) == sign(.upper), "Excludes zero", "Includes zero")) |>
  select(item, contrast, excludes_zero)
```

```{r}
#| fig-height: 5
#| fig-width: 10
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)
rq2.1.7.contrasts |>
  mutate(estimate = estimate * 100) |>
  left_join(rq2.1.7.hdi_check, by = c("item", "contrast")) |>
  ggplot(aes(x = estimate, y = item, fill = excludes_zero)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  stat_slabinterval(
    .width = c(.95),
    point_interval = "median_hdi",
    scale = 0.7,
    slab_alpha = 0.6,        
    interval_alpha = 1,      
    point_alpha = 1,          
    normalize = "groups",
    point_size = 2.5,
    interval_size = 1.5) +
  facet_wrap(~contrast) +
  scale_fill_manual(
    name = "95% HDI",
    values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
  ) +
  # scale_color_manual(
  #   name = "95% HDI",
  #   values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
  # ) +
  scale_x_continuous(limits = c(-15, 15), breaks = seq(-10, 10, by = 5), expand = expansion(add = 2.5)) +
  labs(
    x = "Percentage Points",
    y = NULL,
    title = "Treatment Effects on Political Participation",
    subtitle = "Posterior Distributions with Median and 95% HDI"
  ) +
  theme_nice() +
  theme(
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2),
    legend.position = "bottom"
  )

ggsave(here(figure_dir, "RQ2", "RQ2.1_item_figure.png"),
       height = 5,
       width = 10,
       dpi = 600)
```

## RQ 2.2

```{r}
rq2.2.1 <- readRDS(here(model_dir, "RQ2", "hu1.rds"))
rq2.2.2 <- readRDS(here(model_dir, "RQ2", "hu2.rds"))
rq2.2.3 <- readRDS(here(model_dir, "RQ2", "hu3.rds"))
rq2.2.5 <- readRDS(here(model_dir, "RQ2", "hu5.rds"))
```

### Tables

#### RQ2.2 Model Summary Table

```{r}
rq2.2.1_brms <- broom.mixed::tidy(rq2.2.1, parameters = "b", robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE) |>
  mutate(Model = "Overall")

rq2.2.2_brms <- broom.mixed::tidy(rq2.2.2, parameters = "b", robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE) |>
  mutate(Model = "Age Group")

rq2.2.3_brms <- broom.mixed::tidy(rq2.2.3, parameters = "b", robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE) |>
  mutate(Model = "Gender")

rq2.2_brms <- bind_rows(rq2.2.1_brms, rq2.2.2_brms, rq2.2.3_brms) |>
  filter(!term %in% c("prior_b", "prior_b_hu")) |>
  mutate(
    Parameter = if_else(str_detect(term, "^b_hu_"), "hu", "mu"),
    term = str_remove(term, "^b_hu_"),
    term = str_remove(term, "^b_")
  ) |>
  mutate(term = case_when(
    term == "(Intercept)"                                ~ "Intercept",
    term == "exp_conditionhope"                          ~ "Hope (vs. Control)",
    term == "exp_conditionanxiety"                       ~ "Anxiety (vs. Control)",
    term == "age_group22M26years"                        ~ "Age Group 22-26 (vs. 16-21)",
    term == "exp_conditionhope:age_group22M26years"      ~ "Age Group × Hope",
    term == "exp_conditionanxiety:age_group22M26years"   ~ "Age Group × Anxiety",
    term == "genderfemale"                               ~ "Women (vs. Men)",
    term == "genderother"                                ~ "Other (vs. Men)",
    term == "exp_conditionhope:genderfemale"             ~ "Women × Hope",
    term == "exp_conditionanxiety:genderfemale"          ~ "Women × Anxiety",
    term == "exp_conditionhope:genderother"              ~ "Other × Hope",
    term == "exp_conditionanxiety:genderother"           ~ "Other × Anxiety",
    TRUE ~ term
  )) |>
  select(Parameter, Term = term, Median = estimate, MAD = std.error,
         "95% HDI Lower" = conf.low, "95% HDI Upper" = conf.high,
         "R-hat" = rhat, ESS = ess, Model)

n1 <- rq2.2_brms |> filter(Model == "Overall") |> nrow()
n2 <- rq2.2_brms |> filter(Model == "Age Group") |> nrow()
```

```{r}
rq2.2_brms_table <- rq2.2_brms |>
  mutate(across(where(is.numeric), ~round(.x, 3))) |>
  select(-Model) |>
  tt(notes = "Note. mu = log-normal component (time spent viewing); hu = hurdle component (probability of not viewing).") |>
  group_tt(i = list(
    "Main Model" = 1,
    "Interaction with Age Group" = n1 + 1,
    "Interaction with Gender" = n1 + n2 + 1
  ))

rq2.2_brms_table
rq2.2_brms_table |>
  save_tt(here(table_dir, "RQ2", "rq2.2_brms_table.docx"), overwrite = TRUE)
```

#### RQ2.2 Comparison Table

```{r}
rq2.2.1_hu_comp_raw <- avg_comparisons(rq2.2.1, dpar = "hu", variables = list(exp_condition = "pairwise"))
rq2.2.2_hu_comp_raw <- avg_comparisons(rq2.2.2, dpar = "hu", variables = list(exp_condition = "pairwise"), by = "age_group")
rq2.2.3_hu_comp_raw <- avg_comparisons(rq2.2.3, dpar = "hu", variables = list(exp_condition = "pairwise"), by = "gender")

rq2.2.1_mu_comp_raw <- avg_comparisons(rq2.2.1, dpar = "mu", variables = list(exp_condition = "pairwise"), 
                                       comparison = function(hi, lo) exp(hi) - exp(lo))
rq2.2.2_mu_comp_raw <- avg_comparisons(rq2.2.2, dpar = "mu", variables = list(exp_condition = "pairwise"), by = "age_group", 
                                       comparison = function(hi, lo) exp(hi) - exp(lo))
rq2.2.3_mu_comp_raw <- avg_comparisons(rq2.2.3, dpar = "mu", variables = list(exp_condition = "pairwise"), by = "gender", 
                                       comparison = function(hi, lo) exp(hi) - exp(lo),)

rq2.2.1_hu_comp <- rq2.2.1_hu_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq2.2.1_hu_comp_raw), by = "contrast") |>
  mutate(Model = "Overall", Group = "Overall", Parameter = "hu")

rq2.2.1_mu_comp <- rq2.2.1_mu_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq2.2.1_mu_comp_raw), by = "contrast") |>
  mutate(Model = "Overall", Group = "Overall", Parameter = "mu")

rq2.2.2_hu_comp <- rq2.2.2_hu_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq2.2.2_hu_comp_raw, by = "age_group"), by = c("contrast", "age_group")) |>
  mutate(Model = "Age Group", Parameter = "hu") |>
  rename(Group = age_group)

rq2.2.2_mu_comp <- rq2.2.2_mu_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq2.2.2_mu_comp_raw, by = "age_group"), by = c("contrast", "age_group")) |>
  mutate(Model = "Age Group", Parameter = "mu") |>
  rename(Group = age_group)

rq2.2.3_hu_comp <- rq2.2.3_hu_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq2.2.3_hu_comp_raw, by = "gender"), by = c("contrast", "gender")) |>
  mutate(Model = "Gender", Parameter = "hu") |> 
  rename(Group = gender) 

rq2.2.3_mu_comp <- rq2.2.3_mu_comp_raw |>
  as_tibble() |>
  left_join(probability_direction(rq2.2.3_mu_comp_raw, by = "gender"), by = c("contrast", "gender")) |>
  mutate(Model = "Gender", Parameter = "mu") |>
  rename(Group = gender)

rq2.2_comp <- bind_rows(rq2.2.1_hu_comp, rq2.2.1_mu_comp, rq2.2.2_hu_comp, rq2.2.2_mu_comp, rq2.2.3_hu_comp, rq2.2.3_mu_comp) |>
  mutate(
    Contrast = case_when(
      contrast == "anxiety, control" ~ "Anxiety - Control",
      contrast == "anxiety, hope"    ~ "Anxiety - Hope",
      contrast == "hope, control"    ~ "Hope - Control",
      contrast == "anxiety - control" ~ "Anxiety - Control",
      contrast == "anxiety - hope"    ~ "Anxiety - Hope",
      contrast == "hope - control"    ~ "Hope - Control"),
    Group = case_when(
      Group == "male"   ~ "Men",
      Group == "female" ~ "Women",
      Group == "other"  ~ "Other",
      TRUE ~ Group
    )) |>
  select(Model, Parameter, Group, Contrast,
         Median = estimate,
         "95% HDI Lower" = conf.low,
         "95% HDI Upper" = conf.high,
         "Probability of Direction" = pd)
```

```{r}
rq2.2_comp_table <- rq2.2_comp |> 
  mutate(across(where(is.numeric), ~round(.x, 3))) |> 
  select(-Model) |> 
  tt() |> 
  group_tt(i = list("Main Model" = 1, "By Age Group" = 7, "By Gender" = 19)) 

rq2.2_comp_table

rq2.2_comp_table |> 
  save_tt(here(table_dir, "RQ2", "rq2.2_comp_table.docx"), overwrite = TRUE)
```

#### RQ2.2 Pre-Registration Sample Table

```{r}
rq2.2.5_brms <- broom.mixed::tidy(rq2.2.5, parameters = "b", robust = TRUE, conf.method = "HPDinterval", rhat = TRUE, ess = TRUE) |>
  filter(!term %in% c("prior_b", "prior_b_hu")) |>
  mutate(
    Parameter = if_else(str_detect(term, "^b_hu_"), "hu", "mu"),
    term = str_remove(term, "^b_hu_"),
    term = str_remove(term, "^b_")
  ) |>
  mutate(term = case_when(
    term == "(Intercept)"        ~ "Intercept",
    term == "exp_conditionhope"  ~ "Hope (vs. Control)",
    term == "exp_conditionanxiety" ~ "Anxiety (vs. Control)",
    TRUE ~ term
  )) |>
  select(Parameter, Term = term, Median = estimate, MAD = std.error,
         "95% HDI Lower" = conf.low, "95% HDI Upper" = conf.high,
         "R-hat" = rhat, ESS = ess)
```

```{r}
rq2.2.5_brms_table <- rq2.2.5_brms |>
  mutate(across(where(is.numeric), ~round(.x, 3))) |>
  tt(notes = "Note. mu = log-normal component (time spent viewing); hu = hurdle component (probability of not viewing).")

rq2.2.5_brms_table
rq2.2.5_brms_table |>
  save_tt(here(table_dir, "RQ2", "prereg_RQ2.2.5_brms_table.docx"), overwrite = TRUE)
```

### Figures 

#### Figure Data

```{r}
# Comparisons for hu (decision NOT to view)
rq2.2.1.hu_comparisons <- avg_comparisons(
  rq2.2.1,
  variables = list(exp_condition = "pairwise"),
  dpar = "hu",
  re_formula = NA
) |>
  posterior_draws()

# Format hu comparisons (decision NOT to view)
rq2.2.1.hu_contrasts <- rq2.2.1.hu_comparisons |>
  mutate(
    contrast = case_when(
      contrast == "anxiety - control" ~ "Anxiety − Control",
      contrast == "hope - control" ~ "Hope − Control",
      contrast == "anxiety - hope" ~ "Anxiety - Hope"
    ),
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety − Control", "Hope − Control")),
    model = "ATE",
    subgroup = "ATE",
    estimate = draw
  ) |>
  select(drawid, contrast, estimate, model, subgroup)

# Comparisons for mu (time spent viewing)
rq2.2.1.mu_comparisons <- avg_comparisons(
  rq2.2.1,
  variables = list(exp_condition = "pairwise"),
  dpar = "mu",
  comparison = function(hi, lo) exp(hi) - exp(lo),
  re_formula = NA
) |>
  posterior_draws()

# Format mu comparisons (time spent viewing)
rq2.2.1.mu_contrasts <- rq2.2.1.mu_comparisons |>
  mutate(
    contrast = case_when(
      contrast == "anxiety, control" ~ "Anxiety − Control",
      contrast == "hope, control" ~ "Hope − Control",
      contrast == "anxiety, hope" ~ "Anxiety - Hope"
    ),
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety − Control", "Hope − Control")),
    model = "ATE",
    subgroup = "ATE",
    estimate = draw
  ) |>
  select(drawid, contrast, estimate, model, subgroup)
```

```{r}
# Comparisons for hu (decision NOT to view) by age group
rq2.2.2.hu_comparisons <- avg_comparisons(
  rq2.2.2,
  variables = list(exp_condition = "pairwise"),
  by = "age_group",
  dpar = "hu",
  re_formula = NA
) |>
  posterior_draws()

# Format hu comparisons
rq2.2.2.hu_contrasts <- rq2.2.2.hu_comparisons |>
  mutate(
    contrast = case_when(
      contrast == "anxiety - control" ~ "Anxiety − Control",
      contrast == "hope - control" ~ "Hope − Control",
      contrast == "anxiety - hope" ~ "Anxiety - Hope"
    ),
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety − Control", "Hope − Control")),
    model = "Age",
    subgroup = as.character(age_group),
    estimate = draw
  ) |>
  select(drawid, contrast, estimate, model, subgroup)

# Comparisons for mu (time spent viewing) by age group
rq2.2.2.mu_comparisons <- avg_comparisons(
  rq2.2.2,
  variables = list(exp_condition = "pairwise"),
  by = "age_group",
  dpar = "mu",
  comparison = function(hi, lo) exp(hi) - exp(lo),
  re_formula = NA
) |>
  posterior_draws()

# Format mu comparisons
rq2.2.2.mu_contrasts <- rq2.2.2.mu_comparisons |>
  mutate(
    contrast = case_when(
      contrast == "anxiety, control" ~ "Anxiety − Control",
      contrast == "hope, control" ~ "Hope − Control",
      contrast == "anxiety, hope" ~ "Anxiety - Hope"
    ),
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety − Control", "Hope − Control")),
    model = "Age",
    subgroup = as.character(age_group),
    estimate = draw
  ) |>
  select(drawid, contrast, estimate, model, subgroup)
```

```{r}
# Comparisons for hu (decision NOT to view) by gender
rq2.2.3.hu_comparisons <- avg_comparisons(
  rq2.2.3,
  variables = list(exp_condition = "pairwise"),
  by = "gender",
  dpar = "hu",
  re_formula = NA
) |>
  posterior_draws()

# Format hu comparisons
rq2.2.3.hu_contrasts <- rq2.2.3.hu_comparisons |>
  mutate(
    contrast = case_when(
      contrast == "anxiety - control" ~ "Anxiety − Control",
      contrast == "hope - control" ~ "Hope − Control",
      contrast == "anxiety - hope" ~ "Anxiety - Hope"
    ),
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety − Control", "Hope − Control")),
    model = "Gender",
    subgroup = as.character(gender),
    estimate = draw
  ) |>
  select(drawid, contrast, estimate, model, subgroup)

# rq2.2.3: Comparisons for mu (time spent viewing) by gender
rq2.2.3.mu_comparisons <- avg_comparisons(
  rq2.2.3,
  variables = list(exp_condition = "pairwise"),
  by = "gender",
  dpar = "mu",
  comparison = function(hi, lo) exp(hi) - exp(lo),
  re_formula = NA
) |>
  posterior_draws()

# Format mu comparisons
rq2.2.3.mu_contrasts <- rq2.2.3.mu_comparisons |>
  mutate(
    contrast = case_when(
      contrast == "anxiety, control" ~ "Anxiety − Control",
      contrast == "hope, control" ~ "Hope − Control",
      contrast == "anxiety, hope" ~ "Anxiety - Hope"
    ),
    contrast = factor(contrast, levels = c("Anxiety - Hope", "Anxiety − Control", "Hope − Control")),
    model = "Gender",
    subgroup = as.character(gender),
    estimate = draw
  ) |>
  select(drawid, contrast, estimate, model, subgroup)
```

```{r}
# Combine all hu contrasts and add parameter indicator
rq2.2_hu_posterior_data <- bind_rows(
  rq2.2.1.hu_contrasts,
  rq2.2.2.hu_contrasts,
  rq2.2.3.hu_contrasts
) |>
  mutate(parameter = "hu")

# Combine all mu contrasts and add parameter indicator
rq2.2_mu_posterior_data <- bind_rows(
  rq2.2.1.mu_contrasts,
  rq2.2.2.mu_contrasts,
  rq2.2.3.mu_contrasts
) |>
  mutate(parameter = "mu")

# Combine both parameters
rq2.2_posterior_data <- bind_rows(
  rq2.2_hu_posterior_data,
  rq2.2_mu_posterior_data
) |>
  mutate(
    # Relabel subgroups
    subgroup = case_when(
      subgroup == "male" ~ "Men",
      subgroup == "female" ~ "Women",
      subgroup == "16-21 years" ~ "16-21",
      subgroup == "22-26 years" ~ "22-26",
      TRUE ~ subgroup
    ),
    # Set factor levels
    model = factor(model, levels = c("ATE", "Age", "Gender")),
    subgroup = factor(subgroup, levels = c("ATE", "22-26", "16-21", "Women", "Men"))
  )

# Compute whether HDI excludes zero for each parameter separately
rq2.2_hurdle_check <- rq2.2_posterior_data |>
  group_by(parameter, model, contrast, subgroup) |>
  median_hdi(estimate, .width = 0.95) |>
  mutate(excludes_zero = if_else(sign(.lower) == sign(.upper), "Excludes zero", "Includes zero")) |>
  select(parameter, model, contrast, subgroup, excludes_zero)
```

#### RQ2.2 Figure

##### Decision to View

```{r}
#| fig-height: 5.5
#| fig-width: 9.5
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)

rq2.2_posterior_data |>
  filter(subgroup != "Other") |> 
  filter(parameter == "hu") |>
  mutate(estimate = -estimate * 100) |>  # Flip sign and convert to percentage points
  left_join(
    filter(rq2.2_hurdle_check, parameter == "hu"),
    by = c("parameter", "model", "contrast", "subgroup")
  ) |>
  ggplot(aes(x = estimate, y = subgroup, fill = excludes_zero)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  stat_slabinterval(
    .width = c(.95),
    point_interval = "median_hdi",
    scale = 0.7,
    slab_alpha = 0.6,        
    interval_alpha = 1,      
    point_alpha = 1,          
    normalize = "groups",
    point_size = 2.5,
    interval_size = 1.5) +
  facet_grid(model ~ contrast, scales = "free_y", space = "free_y") +
  scale_fill_manual(
    values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
    name = "95% HDI",
  ) +
  # scale_color_manual(
  #   values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
  #   name = "95% HDI",
  # ) +
  scale_x_continuous(limits = c(-25, 25), breaks = seq(-15, 15, by = 5), expand = expansion(add = 0.5)) +
  labs(
    x = "Percentage Points",
    y = NULL,
    title = "Effects on Initiation of Political Information Seeking",
    subtitle = "Posterior Distributions with Median and 95% HDI"
  ) +
  theme_nice() +
  theme(
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2),
    legend.position = "bottom"
  )

ggsave(here(figure_dir, "RQ2", "RQ2.2_hu_ate_cate.png"),
       height = 5.5,
       width = 9.5,
       dpi = 600)
```

##### Time Spent Viewing

```{r}
#| fig-height: 5.5
#| fig-width: 9.5
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)

rq2.2_posterior_data |>
  filter(subgroup != "Other") |> 
  filter(parameter == "mu") |>
  left_join(
    filter(rq2.2_hurdle_check, parameter == "mu"),
    by = c("parameter", "model", "contrast", "subgroup")
  ) |>
  ggplot(aes(x = estimate, y = subgroup, fill = excludes_zero)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  stat_slabinterval(
    .width = c(.95),
    point_interval = "median_hdi",
    scale = 0.7,
    slab_alpha = 0.6,        
    interval_alpha = 1,      
    point_alpha = 1,          
    normalize = "groups",
    point_size = 2.5,
    interval_size = 1.5) +
  facet_grid(model ~ contrast, scales = "free_y", space = "free_y") +
  scale_fill_manual(
    values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
    name = "95% HDI",
  ) +
  # scale_color_manual(
  #   values = c("Excludes zero" = "#364B9A", "Includes zero" = "#4A7BB7"),
  #   name = "95% HDI",
  # ) +
  scale_x_continuous(limits = c(-8, 8), breaks = seq(-5, 5, by = 2.5), expand = expansion(add = 0.5)) +
  labs(
    x = "Seconds",
    y = NULL,
    title = "Effects on Extent of Political Information Seeking",
    subtitle = "Posterior Distributions with Median and 95% HDI"
  ) +
  theme_nice() +
  theme(
    panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2),
    legend.position = "bottom"
  )
ggsave(here(figure_dir, "RQ2", "RQ2.2_mu_ate_cate.png"),
       height = 5.5,
       width = 9.5,
       dpi = 600)
```

## Combined Figure

```{r}
# Helper to standardise contrast labels and subgroup labels
fix_contrasts <- function(x) {
  x |> str_replace_all("\u2212", "-")  # replace em-dash minus with regular hyphen
}

fix_subgroups <- function(x) {
  case_when(
    x == "female"      ~ "Women",
    x == "male"        ~ "Men",
    x == "16-21 years" ~ "16-21",
    x == "22-26 years" ~ "22-26",
    TRUE               ~ x
  )
}

# RQ1.1 — Democratic Support
rq1.1_clean <- rq1.1_posterior_data |>
  rename(.draw = .draw) |>          # already .draw, just for clarity
  mutate(
    outcome   = "Democratic Support",
    estimate  = estimate * 100,
    contrast  = fix_contrasts(contrast),
    subgroup  = fix_subgroups(subgroup),
    parameter = NA_character_
  ) |>
  select(.draw, contrast, estimate, model, subgroup, outcome, parameter)

# RQ1.2 — Democratic Candidate Choice
rq1.2_clean <- rq1.2_posterior_data |>
  rename(.draw = drawid) |>
  mutate(
    .draw     = as.integer(.draw),
    outcome   = "Democratic Candidate Choice",
    estimate  = estimate * 100,
    contrast  = fix_contrasts(contrast),
    subgroup  = fix_subgroups(subgroup),
    parameter = NA_character_
  ) |>
  select(.draw, contrast, estimate, model, subgroup, outcome, parameter)

# RQ2.1 — Political Participation
rq2.1_clean <- rq2.1_posterior_data |>
  mutate(
    outcome   = "Political Participation",
    estimate  = estimate * 100,
    contrast  = fix_contrasts(contrast),
    subgroup  = fix_subgroups(subgroup),
    parameter = NA_character_
  ) |>
  select(.draw, contrast, estimate, model, subgroup, outcome, parameter)

# RQ2.2 — Information Seeking (hu + mu)
rq2.2_clean <- rq2.2_posterior_data |>
  rename(.draw = drawid) |>
  mutate(
    .draw    = as.integer(.draw),
    contrast = fix_contrasts(contrast),
    subgroup = fix_subgroups(subgroup),
    outcome  = case_when(
      parameter == "hu" ~ "Interest in Democratic Involvement",
      parameter == "mu" ~ "Information Seeking (Time)"
    ),
    estimate = case_when(
      parameter == "hu" ~ -estimate * 100,
      parameter == "mu" ~ estimate
    )
  ) |>
  select(.draw, contrast, estimate, model, subgroup, outcome, parameter)

# Combine
combined_fig_data <- bind_rows(
  rq1.1_clean,
  rq1.2_clean,
  rq2.1_clean,
  rq2.2_clean
) |>
  mutate(
    outcome  = factor(outcome, levels = c(
      "Democratic Support",
      "Democratic Candidate Choice",
      "Political Participation",
      "Interest in Democratic Involvement",
      "Information Seeking (Time)"
    )),
    contrast = factor(contrast, levels = c(
      "Anxiety - Hope",
      "Anxiety - Control",
      "Hope - Control"
    )),
    subgroup = factor(subgroup, levels = c("ATE", "16-21", "22-26", "Women", "Men"))
  )
```

```{r}
combined_fig_data <- combined_fig_data |>
  filter(
    subgroup == "ATE",
    model == "ATE",
    outcome != "Information Seeking (Time)"
  ) |>
  mutate(contrast = fct_rev(contrast)) |>
  group_by(outcome, contrast) |>
  mutate(median_sign = sign(median(estimate))) |>
  ungroup()

pd_data <- combined_fig_data |>
  filter(
    subgroup == "ATE",
    model == "ATE",
    outcome != "Information Seeking (Time)"
  ) |>
  group_by(outcome, contrast) |>
  summarise(
    median_est = median(estimate),
    pd = mean(sign(estimate) == sign(median_est)),
    pd_label = paste0("PD = ", sprintf("%.1f", pd * 100), "%"),
    .groups = "drop"
  ) |>
  mutate(contrast = fct_rev(contrast))  # match the fct_rev in the plot
```


```{r}
#| fig-height: 6
#| fig-width: 8
#| fig-dpi: 600
#| fig-showtext: TRUE
showtext_opts(dpi = 600)

ggplot(combined_fig_data, aes(x = estimate, y = contrast)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40", linewidth = 0.6) +
  # Slab for positive-median groups: concordant = right of zero
  stat_slab(
    data = filter(combined_fig_data, median_sign >= 0),
    aes(fill = after_stat(ifelse(x > 0, "concordant", "discordant"))),
    alpha = 0.8,
    scale = 0.7
  ) +
  # Slab for negative-median groups: concordant = left of zero
  stat_slab(
    data = filter(combined_fig_data, median_sign < 0),
    aes(fill = after_stat(ifelse(x < 0, "concordant", "discordant"))),
    alpha = 0.8,
    scale = 0.7
  ) +
  stat_pointinterval(
    .width = c(0.50, 0.95),
    point_interval = "median_hdi",
    position = position_nudge(y = -0.2),
    color = "grey20",
    point_size = 2
  ) +
  geom_text(
    data = pd_data,
    aes(x = 24.5, y = contrast, label = pd_label),
    hjust = 1,
    vjust = -1,
    size = 4,
    color = "#364B9A",
    family = "Public Sans",
    inherit.aes = FALSE
  ) +
  scale_fill_manual(
    values = c("concordant" = "#364B9A", "discordant" = "#A8C4E0"),
    labels = c("concordant" = "Concordant with median", "discordant" = "Discordant"),
    name = NULL,
    guide = guide_legend(reverse = TRUE)
  ) +
  facet_wrap(~ outcome, nrow = 2, ncol = 2) +
  scale_x_continuous(
    limits = c(-25, 25),
    breaks = seq(-20, 20, by = 5),
    expand = expansion(add = 1)
  ) +
  labs(x = "Percentage Points", y = NULL) +
  theme_nice() +
  theme(panel.grid.major.x = element_line(color = "grey90", linewidth = 0.2),
        legend.position = "none",
        axis.line = element_line(color = "grey25", linewidth = 0.6),
        strip.text = element_text(
          family = "Public Sans Semibold", face = "plain",
          size = rel(0.9),
          hjust = 0.5
      ),
      strip.background = element_rect(fill = "grey95", color = "grey25", linewidth = 0.6))

ggsave(here(figure_dir, "combined_figure.png"),
       height = 6,
       width = 8,
       dpi = 600)
```
















